---
title: "Survey-weighted generalized linear models"
output: 
  html_document:
    theme: paper
    keep_md: yes
    toc: yes
    toc_depth: 2
---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(cache = F, echo = T, warning = F, message = F, tidy = F, size = "small")
rm(list = ls(all.names = TRUE))
library(rmarkdown)
library(dplyr); library(tidyr); library(ggplot2)
library(survey); library(car); library(memisc)
```

```{r load-data, include=FALSE}
## Load data
load("~/git/flu-survey/data/cleaning2.RData")
data <- dataf

#source(recoding.R)
load("~/git/flu-survey/data/recoding.RData")
df <- datar  # datar contains recoded variables
#tail(df)
```

```{r des}
## Create survey object
options(digits = 4)
options(survey.lonely.psu = "adjust")

des <- svydesign(ids = ~1, weights = ~weight, data = df[is.na(df$weight) == F, ])
#summary(des)

```

# Survey questions

## Q1. Before receiving this survey, did you know influenza is different from the stomach flu?
  
### Compare unweighted and weighted sex ratios for Q1
```{r q1}
# unweighted Q1
with(data, addmargins(table(Q1, PPGENDER)))
svyby(~Q1, ~Q1+PPGENDER, des, unwtd.count)
# weighted Q1
svytable(~Q1 + PPGENDER, design = des, round = T)

# unweighted proportion
(u <- with(data, prop.table(table(Q1, PPGENDER), margin = 2))*100)  
# weighted proportion
(w <- prop.table(svytable(~Q1 + PPGENDER, design = des), margin = 2)*100)

# table above with standard errors
ftable(svyby(formula = ~Q1, by = ~PPGENDER, design = des, FUN = svymean, na.rm = T))

```


***

## Q2. Have you had an illness with influenza-like symptoms since August 2015?

### First look at unweighted. Calculate OR for being sick by gender.
```{r q2}
## unweighted
# recode datar$Q2
#head(datar$Q2)

# sick = 1; not sick = 0
df$sick <- car::recode(datar$Q2, recodes = "'Yes' = 1; 'No' = 0; NA = NA")
#head(df$sick)

# unwtd table Q2 by gender
with(df, table(Q2, PPGENDER))

# glm unwtd
fit1 <- glm(sick ~ PPGENDER, data = df, family = binomial())
summary(fit1)
(q2.u <- exp(coefficients(fit1)))  # OR

```

Odds ratio of being sick as a male is `r q2.u[2]` compared to females.


### Apply survey weights for Q2. Calculate OR for getting sick by gender.
```{r des2}
## weighted
# relevel PPGENDER, set male as reference group
df$PPGENDER <- relevel(datar$PPGENDER, "Male")

# update survey object
options(survey.lonely.psu = "adjust")
des2 <- svydesign(ids = ~1, weights = ~weight, data = df)  # data = df

# wtd svyglm
m1 <- svyglm(sick ~ PPGENDER, des2, family = quasibinomial())
summary(m1)

# OR
(or1 <- exp(coefficients(m1)))
# 95% CI 
exp(confint(m1))

```

In the weighted data, females had `r or1[2]` times the odds of being sick compared to males.


### Calculate OR for being sick, adjusted for ethnicity
```{r}
# being sick = 1; by ethnicity; white = reference level
m2 <- svyglm(sick ~ PPETHM, des2, family = quasibinomial())
summary(m2)

# OR adjusted for ethnicity
(or2 <- exp(coefficients(m2)))

# note 95% CI for hispanic group
exp(confint(m2))
```

Compared to whites, OR for being sick are `r or2[2:5]` for blacks, hispanics, others, and 2+ races, respectively.
  
Notes: When a logistic regression is calculated, the regression coefficient (b1) is the estimated increase in the log odds of the outcome per unit increase in the value of the exposure; the exponential function of the regression coefficient (e^b1) is the odds ratio associated with a one-unit increase in the exposure.  


```{r desx}
## should I recode each variable as binomial? or re-level a reference group each time?
## same as above but with recoded 1,0 variables; can change reference level

# first recode xi variables
#summary(datar$PPETHM)
df$white <- car::recode(datar$PPETHM, recodes = "'White, Non-Hispanic' = 1; NA = NA; else = 0")
df$black <- car::recode(datar$PPETHM, recodes = "'Black, Non-Hispanic' = 1; NA = NA; else = 0")
df$hispanic <- car::recode(datar$PPETHM, recodes = "'Hispanic' = 1; NA = NA; else = 0")
df$otherrace <- car::recode(datar$PPETHM, recodes = "'Other, Non-Hispanic' = 1; NA = NA; else = 0")
df$more2race <- car::recode(datar$PPETHM, recodes = "'2+ Races, Non-Hispanic' = 1; NA = NA; else = 0")
#tail(df)

# update survey object mx
options(survey.lonely.psu = "adjust")
desx <- svydesign(ids = ~1, weights = ~weight, data = df)

# being sick; black = 1; not black = 0
mx <- svyglm(sick ~ black, desx, family = quasibinomial())
#summary(mx)
mx2 <- update(mx, ~ . + hispanic)
mx3 <- update(mx2, ~ . + otherrace)
mx4 <- update(mx3, ~ . + more2race)
mx5 <- update(mx4, ~ . + white)  # reference group

# compare
mtable(mx, mx2, mx3, mx4, mx5)
# odds ratios
exp(coefficients(mx5))


## answer: re-level reference group
```

***

### Compare model variables for being sick: adjust for gender, ethnicity, employment, and marital status
```{r des3}
des3 <- svydesign(ids = ~1, weights = ~weight, data = df)

## sick = 1, not sick = 0
# add variables to glm with survey design
a1 <- svyglm(sick ~ PPGENDER, des3, family = quasibinomial())  # by gender
a2 <- update(a1, ~ . + PPETHM)  # adjust for race
a3 <- update(a2, ~ . + work)  #  work
a4 <- update(a3, ~ . + marital)  # marital status

# memisc; can modify summary function
mtable(a1, a2, a3, a4)

# AOR for last glm
exp(coefficients(a4))
```

When adjusting for gender, ethnicity, employment, and marital status, significant variables for being sick included being female (compared to males) and hispanic (compared to white).


***

## Q13. Do you get an influenza vaccine? (Yes, every year; Yes, some years; No, never)

```{r des4}
# first make sure Q13 has been re-grouped
head(datar$Q13)  # original: 3 answers
head(df$q13)  # updated: 2 answers

# relevel q13; no vaccine = reference
df$q13 <- relevel(df$q13, "No")

# update survey object
options(survey.lonely.psu = "adjust")
des4 <- svydesign(ids = ~1, weights = ~weight, data = df)

# getting sick ~ getting vaccine
m <- svyglm(sick ~ q13, des4, family = quasibinomial)
summary(m)

# OR
exp(coefficients(m))
```

Those receiving the vaccine had 1.3231 higher odds of getting sick compared to those who did not get the vaccine.


```{r}
# Q2 + Q13 tables with weights
svytable(~q13 + sick, des4, round = T)  # sick = 1, not sick = 0
(t2 <- prop.table(svytable(~q13 + sick, des4), margin = 2)* 100)
(t1 <- prop.table(svytable(~q13 + sick, des4), margin = 1)* 100)
```

Out of those sick, `r t2[4]`% reported receiving the vaccine.  
Out of those healthy, `r t2[3]`% received the vaccine (`r t2[1]`% did not).  
  
Vaccinated group: `r t1[3]`% report no illness.  
Unvaccinated group: `r t1[1]`% report no illness.  
  

***

### Subset sick + vaccinated group. 
```{r des5}
# subset data for sick and vaccinated
sick_vax <- df %>%
  mutate(sickvax = ifelse((sick == 1 & q13 == "Yes"), 1, 0))

sick_vax$sickvax <- as.factor(sick_vax$sickvax)
str(sick_vax$sickvax)

# table of sick and vaccine status
xtabs(~sick + q13, sick_vax)

# sick and vaccinated = 1, else = 0
table(sick_vax$sickvax)

# update survey object
options(survey.lonely.psu = "adjust")
des5 <- svydesign(ids = ~1, weights = ~weight, data = sick_vax)

## who is getting sick after vaccinations?
# age group
ftable(svyby(~sickvax, ~ppagecat, des5, svymean, na.rm = T))
ftable(svyby(~ppagecat, ~sickvax, des5, svymean, na.rm = T))
# gender
ftable(svyby(~sickvax, ~PPGENDER, des5, svymean, na.rm = T))
ftable(svyby(~PPGENDER, ~sickvax, des5, svymean, na.rm = T))

```


### Run regression and adjust for demographic variables.
```{r}
m1 <- svyglm(sickvax ~ PPGENDER, des5, family = quasibinomial())
m2 <- update(m1, ~ . + PPETHM)
m3 <- update(m2, ~ . + work)
m4 <- update(m3, ~ . + ppagecat)

mtable(m1, m2, m3, m4)  # this isn't very helpful

```


***

## in progress
```{r, eval=FALSE, include=FALSE}
## testing ##

# update survey object
options(survey.lonely.psu = "adjust")
desx <- svydesign(ids = ~1, weights = ~weight, data = df2)

n0 <- svyglm(sick ~ Q11_1 + Q11_2 + Q11_3 + Q11_4 + Q11_5 + Q11_6 + Q11_7
             + Q11_8 + Q11_9 + Q11_10 + Q11_11, desx, family = quasibinomial())

summary(n0)
exp(coefficients(n0))

n1 <- svyglm(sick ~ q13, desx, family = quasibinomial())
n2 <- update(n1, ~ . + PPGENDER + PPETHM)
n3 <- update(n2, ~ . + ppagecat)
mtable(n1, n2, n3)

```

```{r, eval=FALSE, include=FALSE}
## testing analysis ##


```

