---
title: "Analysis summary part 3"
output: 
  html_document:
    fig_caption: yes
    fig_height: 4
    fig_width: 6
    theme: paper
    keep_md: yes
    toc: yes
    toc_depth: 2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T, cache = T, cache.comments = T, warning = F, message = F, tidy = T, size = "small")
rm(list = ls(all.names = TRUE))
library(rmarkdown); library(knitr)
library(tidyr); library(dplyr); library(ggplot2)
library(survey); library(gridExtra)
```

```{r load-data, include=F}
## Load data variables.
load("~/git/flu-survey/data/cleaning2.RData")
load("~/git/flu-survey/data/recoding.RData")  # load "datar"
df <- datar  # contains recoded variables
```

```{r regroup-data, include=FALSE}
## income
income.map <- c(rep("under $10k", 3),
                rep("$10k to $25k", 4),
                rep("$25k to $50k", 4),
                rep("$50k to $75k", 2),
                rep("$75k to $100k", 2),
                rep("$100k to $150k", 2),
                rep("over $150k", 2))
df$income <- code(datar$PPINCIMP, income.map, "under $10k")
income.lab <- c("under $10k", "$10k to $25k", "$25k to $50k", "$50k to $75k", "$75k to $100k", "$100k to $150k", "over $150k")
df$income <- factor(df$income, levels = income.lab)

## marital staus
marital.map <- c("single", "partnered", "partnered", "single", "single", "single")
df$marital <- code(dataf$PPMARIT, marital.map, "single")

## work status
work.map <- c(rep("unemployed", 5),
              rep("employed", 2))
df$work <- code(dataf$PPWORK, work.map, "unemployed")
```

```{r survey-design}
## Create survey object.
options(digits = 4)
options(survey.lonely.psu = "adjust")

# subset data?
des <- svydesign(ids = ~1, weights = ~weight, data = df[is.na(df$weight)==F, ])
```

```{r ggplot, include=FALSE}
#### create ggplot templates ####

ptext <- theme(axis.text = element_text(size = rel(0.9)), axis.text.x = element_text(angle = 45, hjust = 1))
pgen <- aes(PPGENDER)
page <- aes(ppagect4)
peth <- aes(PPETHM)
pinc <- aes(income)
pedu <- aes(PPEDUCAT)
pwor <- aes(work)
pmar <- aes(marital)
er <- geom_errorbar(aes(ymin = Q2Yes - se.Q2Yes, ymax = Q2Yes + se.Q2Yes), width = .25)
```



## Q21. Are influenza vaccines covered by your health insurance?

```{r}

q21 <- as.data.frame(svytable(
  ~Q21 + PPGENDER + ppagect4 + PPETHM + income + PPEDUCAT + work + marital, des, round = T))

p <- ggplot(q21, aes(Q21, weight = Freq)) + ptext
p + geom_bar()

```

### Q22. Do you do any of the following when you have influenza symptoms?
```{r}

```

### Q23. Which of the following actions do you take when you have influenza symptoms to avoid someone else from getting sick?
```{r}

```

### Q24. What sources of information do you recall hearing or seeing about influenza outbreaks?
```{r}

```

### Q25. If you received information from the news, internet or other public media that there was an influenza outbreak in your community would you do any of the following?
```{r}

```

## Q26. Does your household have children?

```{r}
q26 <- as.data.frame(svytable(
  ~Q26 + PPGENDER + ppagect4 + PPETHM + income + PPEDUCAT + work + marital, des, round = T))

p <- ggplot(q26, aes(Q26, weight = Freq)) + ptext
p + geom_bar()

## plot means
svychisq(~Q2 + Q26, des)
q <- svyby(~Q2, ~Q26, des, svymean, na.rm = T)
ggplot(q, aes(Q26, Q2Yes)) + geom_point() + xlab(" ") + ylab("% sick") + er +
  ggtitle(label = "% of adults sick and having children in household") 
```

### Q27. What actions do you take when a child in your household has influenza symptoms?
```{r}

```

## Q28. Are you a single parent?

```{r}
q28 <- as.data.frame(svytable(
  ~Q28 + PPGENDER + ppagect4 + PPETHM + income + PPEDUCAT + work + marital, des, round = T))

p <- ggplot(q28, aes(Q28, weight = Freq)) + ptext
p + geom_bar()


## plot means
svychisq(~Q2 + Q28, des)
q <- svyby(~Q2, ~Q28, des, svymean, na.rm = T)
ggplot(q, aes(Q28, Q2Yes)) + geom_point() + xlab(" ") + ylab("% sick") + er +
  ggtitle(label = "% of adults sick and being single parent") 

```

### Q29. How do you care for a sick child? (married parent)
```{r}

```

### Q30. How do you care for a sick child? (single parent)
```{r}

```

### Q31. How many hours of screen time (time spent watching television, a computer, smartphone, iPad, etc.) do you spend each day on average when you are not sick? Enter 0 if none

```{r}
# histogram


```

### Q32. How many hours of screen time do you spend each day on average when you are sick? Enter 0 if none

```{r}
# histogram


```

### Q33. How many people, including yourself, reside in your household?

```{r}
# histogram


```

