---
title: 'Behavior part 4: Vaccine'
output: 
  html_document:
    fig_height: 4
    fig_width: 6
    theme: paper
    keep_md: yes
    toc: yes
    toc_depth: 2
  html_notebook:  
    theme: paper
    toc: yes
    toc_depth: 2
---

Questions 13-18
Flu vaccine questions.

```{r setup, include=FALSE}
## Setup.
knitr::opts_chunk$set(echo = F, cache = T, cache.comments = F, warning = F, message = F, size = "small")
rm(list = ls(all.names = T))
library(rmarkdown); library(knitr); library(gridExtra)
library(tidyr); library(dplyr); library(ggplot2); library(survey)
```

```{r load-data, include=F}
## Load data.
load("~/git/flu-survey/data/cleaning2.RData")
load("~/git/flu-survey/data/recoding.RData")  # load "datar"
df <- datar  # recoded variables
```

```{r group-data, include=F}
## Regroup variables.
# income
income.map <- c(rep("under $10k", 3), rep("$10k to $25k", 4),
                rep("$25k to $50k", 4), rep("$50k to $75k", 2),
                rep("$75k to $100k", 2), rep("$100k to $150k", 2),
                rep("over $150k", 2))
df$income <- code(datar$PPINCIMP, income.map, "under $10k")
income.lab <- c("under $10k", "$10k to $25k", "$25k to $50k",
                "$50k to $75k", "$75k to $100k", "$100k to $150k",
                "over $150k")
df$income <- factor(df$income, levels = income.lab)

# marital staus
marital.map <- c("single", "partnered", "partnered", "single", "single", "single")
df$marital <- code(dataf$PPMARIT, marital.map, "single")

# work status
work.map <- c(rep("unemployed", 5),
              rep("employed", 2))
df$work <- code(dataf$PPWORK, work.map, "unemployed")
```

```{r des-survey}
## Create survey object.
options(digits = 4)
options(survey.lonely.psu = "adjust")

des <- svydesign(ids = ~1, weights = ~weight, data = df[is.na(df$weight)==F, ])
```

```{r plot-temp, include=F}
## Create ggplot templates.
ptext <- theme(axis.text = element_text(size = rel(0.9)),
               axis.text.x = element_text(angle = 45, hjust = 1))
ptext2 <- ptext + theme(axis.text.x = element_blank())
```



## Q13. Do you get the flu vaccine?

```{r q13}
q13 <- as.data.frame(svytable(~Q13 + PPGENDER + ppagect4 + PPETHM + income + 
    PPEDUCAT + work + marital, des, round = T))

title <- ggtitle("Do you get the flu vaccine?")
p <- ggplot(q13, aes(Q13, weight = Freq)) + ptext
fil <- aes(fill = Q13)

p + geom_bar() + title
```


## Q14. How much do you pay to get an influenza vaccine?

```{r}
q14 <- as.data.frame(svytable(~Q14 + PPGENDER + ppagect4 + PPETHM + income + 
    PPEDUCAT + work + marital, des, round = T))

title <- ggtitle("Q14. How much do you pay to get an influenza vaccine?")
p <- ggplot(q14, aes(Q14, weight = Freq)) + ptext
fil <- aes(fill = Q14)

p + geom_bar() + title
```


## Q15. Are you more likely to get a vaccine if others around you get a vaccine?

```{r}
q15 <- as.data.frame(svytable(~Q15 + PPGENDER + ppagect4 + PPETHM + income + 
    PPEDUCAT + work + marital, des, round = T))

title <- ggtitle("Q15. Are you more likely to get a vaccine if others around you get a vaccine?")
p <- ggplot(q15, aes(Q15, weight = Freq)) + ptext
fil <- aes(fill = Q15)

p + geom_bar() + title
```


## Q16. Are you more likely to get a vaccine if others around you do not get a vaccine?

```{r}
q16 <- as.data.frame(svytable(~Q16 + PPGENDER + ppagect4 + PPETHM + income + 
    PPEDUCAT + work + marital, des, round = T))

title <- ggtitle("Q16. Are you more likely to get a vaccine if others around you do not get a vaccine?")
p <- ggplot(q16, aes(Q16, weight = Freq)) + ptext
fil <- aes(fill = Q16)

p + geom_bar() + title
```


## Q17. Do you get a vaccine to protect yourself, protect others, or protect yourself and others?

```{r}
q17 <- as.data.frame(svytable(~Q17 + PPGENDER + ppagect4 + PPETHM + income + 
    PPEDUCAT + work + marital, des, round = T))

title <- ggtitle("Q17. Do you get a vaccine to protect yourself, protect others, or protect yourself and others?")
p <- ggplot(q17, aes(Q17, weight = Freq)) + ptext
fil <- aes(fill = Q17)

p + geom_bar() + title
```


## Q18. What are the reasons you would not get an influenza vaccine?

```{r q18-data}
# subset question data, rename columns, gather into single column
q18_df <- df %>%
  select(CaseID, PPGENDER, PPAGE, ppagecat, PPETHM, PPINCIMP, PPEDUC, PPEDUCAT,
         work, PPWORK, marital, PPMARIT, PPMSACAT, ppreg9, PPSTATEN, PPHOUSE, PPRENT, PPNET, Q18_1:Q18_10, weight) %>%
  gather(Q18_q, Q18_r, Q18_1:Q18_10, na.rm = T) %>%
  mutate(Q18_q = as.factor(Q18_q))

# survey design
options(digits = 4)
options(survey.lonely.psu = "adjust")
des18 <- svydesign(ids = ~1, weights = ~weight, data = q18_df[is.na(q18_df$weight)==F, ])
```

### Gender, age, ethnicity, income

```{r q18-plot-1}
# weighted data frame
q18 <- data.frame(svytable(~Q18_q + Q18_r + PPGENDER + ppagecat + PPETHM + PPINCIMP, des18, round = T))

# plot templates
title <- ggtitle("Which of the following actions do you take when you have influenza symptoms to avoid someone else from getting sick?")

## main plot
p <- ggplot(q18, aes(Q18_q, weight = Freq)) + ptext
p + geom_bar(position = 'fill') + aes(fill = Q18_r) + title
```

```{r q18-plot-1b}
p2 <- ggplot(q18, aes(Q18_q, weight = Freq)) + ptext
p2 + geom_bar(position = "fill") + aes(Q18_q, fill = Q18_r)
p2 + geom_bar() + aes(Q18_r, fill = Q18_r) + facet_wrap(~Q18_q) + ptext2
p2 + geom_bar() + aes(Q18_q, fill = Q18_q) + facet_wrap(~Q18_r) + ptext2

# by gender
p2 + geom_bar() + aes(PPGENDER, fill = Q18_r) + facet_wrap(~Q18_q) + ggtitle("By gender")
p2 + geom_bar(position = "fill") + aes(PPGENDER, fill = Q18_r) + facet_wrap(~Q18_q)
p2 + geom_bar() + aes(Q18_q, fill = PPGENDER) + facet_wrap(~Q18_r)
p2 + geom_bar(position = 'fill') + aes(Q18_q, fill = PPGENDER) + facet_wrap(~Q18_r) + ggtitle("By gender")
p2 + geom_bar() + aes(PPGENDER, fill = PPGENDER) + facet_grid(Q18_q~Q18_r) + coord_flip() + ptext2

# by age group
p2 + geom_bar() + aes(ppagecat, fill = Q18_r) + facet_wrap(~Q18_q) + ggtitle("By age group")
p2 + geom_bar(position = "fill") + aes(ppagecat, fill = Q18_r) + facet_wrap(~Q18_q)
p2 + geom_bar() + aes(Q18_q, fill = ppagecat) + facet_wrap(~Q18_r)
p2 + geom_bar(position = 'fill') + aes(Q18_q, fill = ppagecat) + facet_wrap(~Q18_r) + ggtitle("By age group")
p2 + geom_bar() + aes(ppagecat, fill = ppagecat) + facet_grid(Q18_q~Q18_r) + ptext2

# by ethnic group
p2 + geom_bar() + aes(PPETHM, fill = Q18_r) + facet_wrap(~Q18_q) + ggtitle("By ethnic group")
p2 + geom_bar(position = "fill") + aes(PPETHM, fill = Q18_r) + facet_wrap(~Q18_q)
p2 + geom_bar() + aes(Q18_q, fill = PPETHM) + facet_wrap(~Q18_r)
p2 + geom_bar(position = 'fill') + aes(Q18_q, fill = PPETHM) + facet_wrap(~Q18_r) + ggtitle("By ethnic group")
p2 + geom_bar() + aes(PPETHM, fill = PPETHM) + facet_grid(Q18_q~Q18_r) + ptext2
p2 + geom_bar() + aes(Q18_r, fill = Q18_r) + facet_grid(Q18_q~PPETHM) + ptext2

# by income
p2 + geom_bar() + aes(PPINCIMP, fill = Q18_r) + facet_wrap(~Q18_q) + ggtitle("By income") + ptext2
p2 + geom_bar(position = "fill") + aes(PPINCIMP, fill = Q18_r) + facet_wrap(~Q18_q) + ptext2
p2 + geom_bar() + aes(Q18_q, fill = PPINCIMP) + facet_wrap(~Q18_r)
p2 + geom_bar(position = 'fill') + aes(Q18_q, fill = PPINCIMP) + facet_wrap(~Q18_r) + ggtitle("By income group")
p2 + geom_bar() + aes(PPINCIMP, fill = PPINCIMP) + facet_grid(Q18_q~Q18_r) + ptext2

```

### Education, work, marital status

```{r q18-plot-2}
# update weighted data frame
q18.2 <- data.frame(svytable(~Q18_q + Q18_r + PPEDUC + PPEDUCAT + work + PPWORK + marital + PPMARIT, des18, round = T))

# restate plots
p3 <- ggplot(q18.2, aes(Q18_q, weight = Freq)) + ptext
```

```{r q18-plot-2b}
# by education
p3 + geom_bar() + aes(PPEDUCAT, fill = Q18_r) + facet_wrap(~Q18_q) + ggtitle("By education")
p3 + geom_bar(position = "fill") + aes(PPEDUCAT, fill = Q18_r) + facet_wrap(~Q18_q)
p3 + geom_bar() + aes(Q18_q, fill = PPEDUCAT) + facet_wrap(~Q18_r)
p3 + geom_bar(position = "fill") + aes(Q18_q, fill = PPEDUCAT) + facet_wrap(~Q18_r) + ggtitle("By education")
p3 + geom_bar() + aes(PPEDUCAT, fill = PPEDUCAT) + facet_grid(Q18_q~Q18_r) + ptext2
p3 + geom_bar() + aes(Q18_r, fill = Q18_r) + facet_grid(Q18_q~PPEDUCAT) + ptext2

# by work
p3 + geom_bar() + aes(work, fill = Q18_r) + facet_wrap(~Q18_q) + ggtitle("By employment status")
p3 + geom_bar(position = "fill") + aes(work, fill = Q18_r) + facet_wrap(~Q18_q)

# by marital
p3 + geom_bar() + aes(marital, fill = Q18_r) + facet_wrap(~Q18_q) + ggtitle("By marital status")
p3 + geom_bar(position = "fill") + aes(marital, fill = Q18_r) + facet_wrap(~Q18_q)

```

### Metro status, region, state, house type, housing status, internet availability

```{r q18-plot-3}
# update weighted data frame
q18.3 <- data.frame(svytable(~Q18_q + Q18_r + PPMSACAT + ppreg9 + PPSTATEN + PPHOUSE + PPRENT + PPNET, des18, round = T))

# restate plots
p4 <- ggplot(q18.3, aes(Q18_q, weight = Freq)) + ptext
```

```{r q18-plot-3b}
# by metro status
p4 + geom_bar(position = "fill") + aes(Q18_r, fill = PPMSACAT) + facet_wrap(~Q18_q) + ggtitle("By metro status")
p4 + geom_bar(position = "fill") + aes(PPMSACAT, fill = Q18_r) + facet_wrap(~Q18_q)

# by region
p4 + geom_bar(position = "fill") + aes(Q18_r, fill = ppreg9) + facet_wrap(~Q18_q) + ggtitle("By region")
p4 + geom_bar() + aes(ppreg9, fill = Q18_r) + facet_wrap(~Q18_q) + ggtitle("By region")

# by state
p4 + geom_bar() + aes(Q18_r, fill = PPSTATEN) + facet_wrap(~Q18_q) + ggtitle("By state")
p4 + geom_bar() + aes(PPSTATEN, fill = Q18_q) + coord_flip() + ggtitle("By state")

# by house type
p4 + geom_bar(position = "fill") + aes(Q18_r, fill = PPHOUSE) + facet_wrap(~Q18_q)
p4 + geom_bar(position = "fill") + aes(fill = PPHOUSE) + ggtitle("By house type")

# housing status
p4 + geom_bar(position = "fill") + aes(Q18_r, fill = PPHOUSE) + facet_wrap(~Q18_q)
p4 + geom_bar() + aes(PPHOUSE, fill = Q18_r) + facet_wrap(~Q18_q) + ggtitle("By housing")

# by internet availability
p4 + geom_bar(position = "fill") + aes(Q18_r, fill = PPNET) + facet_wrap(~Q18_q)
p4 + geom_bar(position = "fill") + aes(PPNET, fill = Q18_r) + facet_wrap(~Q18_q) + ggtitle("By internet availability")

```




