---
title: "pre-analysis"
output: 
  html_document:
    keep_md: yes
    theme: paper
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(cache=F, echo=T, warning=F, message=F, tidy=F, size="small")
rm(list = ls(all.names = TRUE))
library(dplyr); library(ggplot2); library(survey); library(gridExtra); library(rmarkdown)
```

```{r}
## Load data
load("~/git/flu-survey/data/cleaning2.RData")  # dat = original, dataf = renamed columns
load("~/git/flu-survey/data/recoding.RData")  # datar = regrouped variables

df <- datar  # regrouped data set
```

```{r des}
# Survey package: http://faculty.washington.edu/tlumley/survey-jsm-nup.pdf

## Create survey object
options(digits = 4)
options(survey.lonely.psu = "adjust")

des <- svydesign(ids = ~1, weights = ~weight, data = df[is.na(df$weight) == F, ])  # nest?

# ids = ~1 specifies independent sampling

```

### Ex: Unweighted vs. weighted survey data
See unwtd/wtd frequency tables from original report.

```{r ex1}
# unwtd count for gender
svyby(~CaseID, ~PPGENDER, des, unwtd.count)
# wtd gender
as.data.frame(svytable(~PPGENDER, design = des))

# unwtd count for ethnicity
svyby(~CaseID, ~PPETHM, des, unwtd.count)
# wtd ethnicity
as.data.frame(svytable(~PPETHM, design = des))

# unwtd count for age group
svyby(~CaseID, ~ppagecat, des, unwtd.count)
# wtd age group
as.data.frame(svytable(~ppagecat, design = des))

# age plots
opar <- par(mfrow = c(1,2))
hist(df$PPAGE, main = "Unweighted age", ylim=c(0,300))
svyhist(~PPAGE, des, main = "Weighted age", probability = F, ylim=c(0,300))

# age and gender
boxplot(PPAGE~PPGENDER, df, main = "Unweighted age & gender")
svyboxplot(PPAGE~PPGENDER, des, main = "Weighted age & gender")
par(opar)

```

### Ex tables: Q1 by gender

```{r ex2}
# unwtd count
ftable(svyby(~CaseID, ~Q1+PPGENDER, des, unwtd.count))
# same as
with(df, table(Q1, PPGENDER))

# wtd count
svytable(~Q1 + PPGENDER, design = des)
# wtd count (rounded)
svytable(~Q1 + PPGENDER, design = des, round = T)

# unwtd proportion
with(df, prop.table(table(Q1, PPGENDER), margin = 1))
# wtd proportion
ftable(svyby(~PPGENDER, ~Q1, design = des, FUN = svymean, na.rm = T))

```

### Ex plots

```{r ex3}
# default mosaic plot
plot(svytable(~Q1 + PPGENDER, des), main = "Mosaic plot of Q1 & gender")

# fourfold plot shows associations across a set of 2x2 tables
fourfoldplot(svytable(~Q2 + PPGENDER, des), std = "ind.max", main = "Fourfold plot of Q2 & gender")

```


Demographic variables include: gender, ethnicity, age, education, income, employment, marital status, metro location, region, house type, head of household, rent status, state, internet availability


## Q1. Before receiving this survey did you know influenza is different from the stomach flu?

### Compare by gender, ethnicity, age group, education, income, region, internet availabiliy.

```{r q1}
# save svytable as data frame
q1 <- as.data.frame(svytable(~Q1 + PPGENDER + PPETHM + ppagecat, des, round = T))

# make ggplot objects
title <- ggtitle("Did you know influenza is different from the stomach flu?")
g <- ggplot(q1, aes(weight = Freq))

# plots
#svytable(~Q1 + PPGENDER, des, round = T)
(a <- g + aes(PPGENDER, fill = Q1) + geom_bar(width = 0.7, position = "dodge") + title)
#svytable(~Q1 + PPETHM, des, round = T)
(b <- g + aes(PPETHM, fill = Q1) + geom_bar(width = 0.7, position = "stack") +
  geom_point(aes(y = -0.05), size = 0.75, alpha = 0.3, position = position_jitter(h = 0.01)) + title)
#svytable(~Q1 + ppagecat, des, round = T)
(c <- g + aes(ppagecat, fill = Q1) + geom_bar(position = "fill") +
  geom_point(aes(y = -0.05), size = 0.75, alpha = 0.3, position = position_jitter(h = 0.01)) + title)

## weighted plots
grid.arrange(a, b, c)

```

```{r q1a}
# dataframe
q1 <- as.data.frame(svytable(~Q1 + PPEDUC + PPINCIMP + ppreg9 + PPNET, des, round = T))
g <- ggplot(q1, aes(weight = Freq))

# more plots
g + aes(PPEDUC, fill = Q1) + geom_bar(width = 0.7, position = "dodge") + title
g + aes(PPINCIMP, fill = Q1) + geom_bar(width = 0.7, position = "dodge") + title
g + aes(ppreg9, fill = Q1) + geom_bar(width = 0.7, position = "dodge") + title
g + aes(PPNET, fill = Q1) + geom_bar(width = 0.7, position = "dodge") + title

```

### Compare to unweighted plots.

```{r}
## unweighted plots
q <- ggplot(df[!is.na(df$Q1), ])

with(df, table(PPGENDER, Q1))
d <- q + geom_bar(aes(PPGENDER, fill = Q1), position = "dodge")
with(df, table(PPETHM, Q1))
e <- q + geom_bar(aes(Q1, fill = PPETHM), position = "dodge")
with(df, table(ppagecat, Q1))
f <- q + geom_bar(aes(Q1, fill = ppagecat), position = "dodge")

# unweighted
grid.arrange(d, e, f)
```

### Examine the % of US adults sick with ILI last year by gender, ethnicity, and age. Do a survey-corrected chi-square test for independence.

```{r chisq}
## % of US adults sick last year with ILI by gender
sex <- svyby(formula = ~Q2, by = ~PPGENDER, design = des, FUN = svymean, na.rm = T)
svychisq(~Q2 + PPGENDER, design = des)

qplot(x = sex$PPGENDER, y = sex$Q2Yes, data = sex, xlab = "sex", ylab = "% sick") + geom_errorbar(aes(x = PPGENDER, ymin = Q2Yes - se.Q2Yes, ymax = Q2Yes + se.Q2Yes), width = .25) + ggtitle(label = "% of adults sick last year with ILI by sex")

## % of US adults sick last year with ILI by ethnicity
eth <- svyby(formula = ~Q2, by = ~PPETHM, design = des, FUN = svymean, na.rm = T)
svychisq(~Q2 + PPETHM, design = des)

qplot(x = eth$PPETHM, y = eth$Q2Yes, data = eth, xlab = "ethnicity", ylab = "% sick") + geom_errorbar(aes(x = PPETHM, ymin = Q2Yes - se.Q2Yes, ymax = Q2Yes + se.Q2Yes), width = .25) + ggtitle(label = "% of adults sick last year with ILI by ethnicity")

## % of US adults sick last year with ILI by age
age <- svyby(formula = ~Q2, by = ~ppagecat, design = des, FUN = svymean, na.rm = T)
svychisq(~Q2 + ppagecat, design = des)

qplot(x = age$ppagecat, y = age$Q2Yes, data = age, xlab = "age", ylab = "% sick") + geom_errorbar(aes(x = ppagecat, ymin = Q2Yes - se.Q2Yes, ymax = Q2Yes + se.Q2Yes), width = .25) + ggtitle(label = "% of adults sick last year with ILI by age")
```




