---
title: "Behavior part 1: Transportation"
output: 
  html_document:
    fig_caption: yes
    keep_md: yes
    theme: paper
    toc: yes
    toc_depth: 2
---

Questions 7, 8, 9, 10.
Transportation behavior.

```{r setup, include=FALSE}
## Setup.

knitr::opts_chunk$set(echo = F, cache = T, warning = F, message = F, size = "small")
rm(list = ls(all.names = T))
library(rmarkdown); library(knitr); library(gridExtra)
library(tidyr); library(dplyr); library(ggplot2); library(survey)
```

```{r load-data, include=F}
## Load data.

load("~/git/flu-survey/data/cleaning2.RData")
load("~/git/flu-survey/data/recoding.RData")  # load "datar"
df <- datar  # recoded variables
```

```{r group-data, include=F}
## Regroup variables.

# income
income.map <- c(rep("under $10k", 3), rep("$10k to $25k", 4),
                rep("$25k to $50k", 4), rep("$50k to $75k", 2),
                rep("$75k to $100k", 2), rep("$100k to $150k", 2),
                rep("over $150k", 2))
df$income <- code(datar$PPINCIMP, income.map, "under $10k")
income.lab <- c("under $10k", "$10k to $25k", "$25k to $50k",
                "$50k to $75k", "$75k to $100k", "$100k to $150k",
                "over $150k")
df$income <- factor(df$income, levels = income.lab)

# marital staus
marital.map <- c("single", "partnered", "partnered", "single", "single", "single")
df$marital <- code(dataf$PPMARIT, marital.map, "single")

# work status
work.map <- c(rep("unemployed", 5),
              rep("employed", 2))
df$work <- code(dataf$PPWORK, work.map, "unemployed")
```

```{r des-survey}
## Create survey object.

options(digits = 4)
options(survey.lonely.psu = "adjust")

des <- svydesign(ids = ~1, weights = ~weight, data = df[is.na(df$weight)==F, ])
```

```{r plot-temp, include=F}
## Create ggplot templates.

ptext <- theme(axis.text = element_text(size = rel(0.9)),
               axis.text.x = element_text(angle = 45, hjust = 1))

```


## Q7. What types of public transportation do you regularly use?

```{r q7-data}
# subset question data, rename columns, gather into single column
q7_df <- df %>%
  select(CaseID, PPGENDER, PPAGE, ppagecat, PPETHM, PPINCIMP, PPEDUC, PPEDUCAT,
         work, marital, PPMSACAT, ppreg9, PPSTATEN, PPHOUSE, PPNET,
         Q7_1:Q7_7, Q7_otherText, weight) %>%
  rename(Bus = Q7_1, Carpool = Q7_2, Subway = Q7_3, Train = Q7_4,
         Taxi = Q7_5, Airplane = Q7_6, Other = Q7_7) %>%
  gather(Q7_q, Q7_r, Bus:Other, na.rm = T) %>%
  mutate(Q7_q = as.factor(Q7_q))

# select only Yes responses
q7_df <- q7_df[(q7_df$Q7_r)=='Yes', ]
str(q7_df)

# survey design
des7 <- svydesign(ids = ~1, weights = ~weight, data = q7_df[is.na(q7_df$weight)==F, ])
```

Gender, age, ethnicity, income, education

```{r q7-plot-1}
# weighted data frame
q7 <- data.frame(svytable(~Q7_q + Q7_r + PPGENDER + ppagecat + PPETHM +
                            PPINCIMP + PPEDUC + PPEDUCAT, des7, round = T))
# plot templates
title <- ggtitle("What types of public transportation do you regularly use?")
p <- ggplot(q7[(q7$Q7_r)=='Yes', ], aes(Q7_q, weight = Freq)) + ptext

# main plot
p + geom_bar() + title
```

```{r q7-plot-2}
# exclude "Other" choice
p2 <- ggplot(q7[!(q7$Q7_q)=='Other', ], aes(Q7_q, weight = Freq)) + ptext

# by gender
p2 + geom_bar() + aes(PPGENDER, fill = PPGENDER) + facet_wrap(~Q7_q) + ggtitle("By gender")

# by age group
p2 + geom_bar() + aes(ppagecat, fill = ppagecat) + facet_wrap(~Q7_q) + ggtitle("By age group")
p2 + geom_bar(position = "fill") + aes(ppagecat, fill = Q7_q)

# by ethnic group
p + geom_bar() + aes(PPETHM, fill = PPETHM) + facet_wrap(~Q7_q) +
  ggtitle("By ethnic group") + theme(axis.text.x = element_blank())
p + geom_bar() + aes(fill = Q7_q) + facet_grid(~PPETHM) +
  ggtitle("By ethnic group")

# by income
p + geom_bar() + aes(PPINCIMP, fill = PPINCIMP) + facet_grid(~Q7_q) +
  ggtitle("By income") + theme(axis.text.x = element_blank())

# by education
```

Employment status, marital status, metro status, region, state of residency, housing status, internet availability

```{r q7-plot-3}
# weighted data frame
q7 <- data.frame(svytable(~Q7_q + Q7_r + work + marital + PPMSACAT +
                            ppreg9 + PPSTATEN + PPHOUSE + PPNET, des7, round = T))
# p and p2
p <- ggplot(q7[(q7$Q7_r)=='Yes', ], aes(Q7_q, weight = Freq)) + ptext
p2 <- ggplot(q7[!(q7$Q7_q)=='Other', ], aes(Q7_q, weight = Freq)) + ptext
```

```{r}
# by work
p + geom_bar() + aes(work, fill = work) + facet_wrap(~Q7_q) + ggtitle("By employment status")

# by marital
p + geom_bar() + aes(marital, fill = marital) + facet_wrap(~Q7_q) + ggtitle("By marital status")
p + geom_bar(position = "fill") + aes(marital, fill = Q7_q)

# by metro status
p + geom_bar(position = "fill") + aes(fill = PPMSACAT)

# by region
p + geom_bar() + aes(fill = ppreg9)

# by state
p + geom_bar() + aes(PPSTATEN, fill = Q7_q) + coord_flip()

# by house type
p + geom_bar(position = "fill") + aes(fill = PPHOUSE)

# by internet availability
p + geom_bar(position = "fill") + aes(fill = PPNET)

```



## Q8. For what types of activities do you regularly use public transportation?

```{r q8-data}
# subset question data, rename columns, gather into single column
q8_df <- df %>%
  select(CaseID, PPGENDER, PPAGE, ppagecat, PPETHM, PPINCIMP, PPEDUC, PPEDUCAT,
         work, marital, PPMSACAT, ppreg9, PPSTATEN, PPHOUSE, PPNET,
         Q8_1:Q8_6, Q8_otherText, weight) %>%
  rename(Work = Q8_1, School = Q8_2, Shopping = Q8_3, Visiting_people = Q8_4,
         Recreation = Q8_5, Other = Q8_6) %>%
  gather(Q8_q, Q8_r, Work:Other, na.rm = T) %>%
  mutate(Q8_q = as.factor(Q8_q))

# select only Yes responses
q8_df <- q8_df[(q8_df$Q8_r)=='Yes', ]
str(q8_df)

# survey design
des8 <- svydesign(ids = ~1, weights = ~weight, data = q8_df[is.na(q8_df$weight)==F, ])
```

Gender, age, ethnicity, income, education

```{r q8-plot-1}
# weighted data frame
q8 <- data.frame(svytable(~Q8_q + Q8_r + PPGENDER + ppagecat + PPETHM +
                            PPINCIMP + PPEDUC + PPEDUCAT, des8, round = T))
# plot templates
title <- ggtitle("For what types of activities do you regularly use public transportation?")
p <- ggplot(q8[(q8$Q8_r)=='Yes', ], aes(Q8_q, weight = Freq)) + ptext

# main plot
p + geom_bar() + title
```

```{r}
# exclude "Other" choice
p2 <- ggplot(q8[!(q8$Q8_q)=='Other', ], aes(Q8_q, weight = Freq)) + ptext

# by gender
p2 + geom_bar() + aes(PPGENDER, fill = PPGENDER) + facet_wrap(~Q8_q) + ggtitle("By gender")

# by age group
p2 + geom_bar() + aes(ppagecat, fill = ppagecat) + facet_wrap(~Q8_q) + ggtitle("By age group")
p2 + geom_bar(position = "fill") + aes(ppagecat, fill = Q8_q)

# by ethnic group
p + geom_bar() + aes(PPETHM, fill = PPETHM) + facet_wrap(~Q8_q) +
  ggtitle("By ethnic group") + theme(axis.text.x = element_blank())
p + geom_bar() + aes(fill = Q8_q) + facet_grid(~PPETHM) +
  ggtitle("By ethnic group")

# by income
p + geom_bar() + aes(PPINCIMP, fill = PPINCIMP) + facet_grid(~Q8_q) +
  ggtitle("By income") + theme(axis.text.x = element_blank())

# by education
```

Employment status, marital status, metro status, region, state of residency, housing status, internet availability

```{r q8-plot-3}
# weighted data frame
q8 <- data.frame(svytable(~Q8_q + Q8_r + work + marital + PPMSACAT +
                            ppreg9 + PPSTATEN + PPHOUSE + PPNET, des8, round = T))
# p and p2
p <- ggplot(q8[(q8$Q8_r)=='Yes', ], aes(Q8_q, weight = Freq)) + ptext
p2 <- ggplot(q8[!(q8$Q8_q)=='Other', ], aes(Q8_q, weight = Freq)) + ptext
```

```{r}
# by work
p + geom_bar() + aes(work, fill = work) + facet_wrap(~Q8_q) + ggtitle("By employment status")

# by marital
p + geom_bar() + aes(marital, fill = marital) + facet_wrap(~Q8_q) + ggtitle("By marital status")
p + geom_bar(position = "fill") + aes(marital, fill = Q8_q)

# by metro status
p + geom_bar(position = "fill") + aes(fill = PPMSACAT) + ggtitle("By metro status")

# by region
p + geom_bar() + aes(fill = ppreg9) + ggtitle("By region")

# by state
p + geom_bar() + aes(PPSTATEN, fill = Q8_q) + coord_flip() + ggtitle("By state")

# by house type
p + geom_bar(position = "fill") + aes(fill = PPHOUSE) + ggtitle("By housing type")

# by internet availability
p + geom_bar(position = "fill") + aes(fill = PPNET) + ggtitle("By internet status")
```



## Q9. Do other members of your household regularly use public transportation?

```{r q9}
# weighted data frame
q9 <- data.frame(svytable(~Q9 + PPETHM + income + PPMSACAT, des, round = T))

# plot templates
title <- ggtitle("Do other members of your household regularly use public transportation?")
p <- ggplot(q9, aes(Q9, weight = Freq)) + ptext

# main plot
p + geom_bar() + title
```



## Q10. What types of public transportation do other members of your household regularly use?

```{r q10-data}
# subset question data, rename columns, gather into single column
q10_df <- df %>%
  select(CaseID, PPGENDER, PPAGE, ppagecat, PPETHM, PPINCIMP, PPEDUC, PPEDUCAT,
         work, marital, PPMSACAT, ppreg9, PPSTATEN, PPHOUSE, PPNET,
       Q10_1:Q10_8, Q10_otherText, weight) %>%
  rename(Bus = Q10_1, Carpool = Q10_2, Subway = Q10_3, Train = Q10_4,
         Taxi = Q10_5, Airplane = Q10_6, Dont_know = Q10_7, Other = Q10_8) %>%
  gather(Q10_q, Q10_r, Bus:Other, na.rm = T) %>%
  mutate(Q10_q = as.factor(Q10_q))

# select only Yes responses
q10_df <- q10_df[(q10_df$Q10_r)=='Yes', ]
str(q10_df)

# survey design
des10 <- svydesign(ids = ~1, weights = ~weight, data = q10_df[is.na(q10_df$weight)==F, ])
```

Gender, age, ethnicity, income, education

```{r}
# weighted data frame
q10 <- data.frame(svytable(~Q10_q + Q10_r + PPGENDER + ppagecat + PPETHM +
                             PPINCIMP + PPEDUC + PPEDUCAT, des10, round = T))
# plot templates
title <- ggtitle("What types of public transportation do other members of your household regularly use?")
p <- ggplot(q10[(q10$Q10_r)=='Yes', ], aes(Q10_q, weight = Freq)) + ptext

# main plot
p + geom_bar() + title
```

```{r}
# exclude "Other" choice
p2 <- ggplot(q10[!(q10$Q10_q)=='Other', ], aes(Q10_q, weight = Freq)) + ptext

# by gender
p2 + geom_bar() + aes(PPGENDER, fill = PPGENDER) + facet_wrap(~Q10_q) + ggtitle("By gender")

# by age group
p2 + geom_bar() + aes(ppagecat, fill = ppagecat) + facet_wrap(~Q10_q) + ggtitle("By age group")
p2 + geom_bar(position = "fill") + aes(ppagecat, fill = Q10_q)

# by ethnic group
p + geom_bar() + aes(PPETHM, fill = PPETHM) + facet_wrap(~Q10_q) +
  ggtitle("By ethnic group") + theme(axis.text.x = element_blank())
p + geom_bar() + aes(fill = Q10_q) + facet_grid(~PPETHM) +
  ggtitle("By ethnic group")

# by income
p + geom_bar() + aes(PPINCIMP, fill = PPINCIMP) + facet_grid(~Q10_q) +
  ggtitle("By income") + theme(axis.text.x = element_blank())

# by education
```

Employment status, marital status, metro status, region, state of residency, housing status, internet availability

```{r}
# weighted data frame
q10 <- data.frame(svytable(~Q10_q + Q10_r + work + marital + PPMSACAT +
                            ppreg9 + PPSTATEN + PPHOUSE + PPNET, des10, round = T))
# p and p2
p <- ggplot(q10[(q10$Q10_r)=='Yes', ], aes(Q10_q, weight = Freq)) + ptext
p2 <- ggplot(q10[!(q10$Q10_q)=='Other', ], aes(Q10_q, weight = Freq)) + ptext
```

```{r}
# by work
p + geom_bar() + aes(work, fill = work) + facet_wrap(~Q10_q) + ggtitle("By employment status")

# by marital
p + geom_bar() + aes(marital, fill = marital) + facet_wrap(~Q10_q) + ggtitle("By marital status")
p + geom_bar(position = "fill") + aes(marital, fill = Q10_q)

# by metro status
p + geom_bar(position = "fill") + aes(fill = PPMSACAT) + ggtitle("By metro status")

# by region
p + geom_bar() + aes(fill = ppreg9) + ggtitle("By region")

# by state
p + geom_bar() + aes(PPSTATEN, fill = Q10_q) + coord_flip() + ggtitle("By state")

# by house type
p + geom_bar(position = "fill") + aes(fill = PPHOUSE) + ggtitle("By house type")

# by internet availability
p + geom_bar(position = "fill") + aes(fill = PPNET) + ggtitle("By internet availability")
```



