---
title: "Models"
output:
  html_document:
    df_print: kable
    number_sections: yes
    theme: paper
    toc: yes
  pdf_document:
    toc: yes
editor_options:
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = '../../')
rm(list = ls())
```

```{r}
library(survey)

source('flu-survey/analysis/chendaniely/model_utils.R')

load('flu-survey/data/model_dataframes.RData')

svy_never_every     <- svydesign(ids = ~1, weights = ~weight, data = never_every[!is.na(never_every$weight), ])
svy_never_some      <- svydesign(ids = ~1, weights = ~weight, data = never_some[!is.na(never_some$weight), ])
svy_never_someevery <- svydesign(ids = ~1, weights = ~weight, data = never_someevery[!is.na(never_someevery$weight), ])
svy_some_every      <- svydesign(ids = ~1, weights = ~weight, data = some_every[!is.na(some_every$weight), ])
```

# Demographic model
Demographics + Q13

- ppagecat
- PPEDUCAT
- income
- PPREG4
- work

## Every vs. never (referent)
```{r}
ne_demo <- svyglm(formula = Q13 ~ ppagecat + PPEDUCAT + income + PPREG4 + work,
       design = svy_never_every,
       family = quasibinomial(link = "logit"))
print_svy_mod(ne_demo)
```
## Some vs. never
```{r}
ns_demo <- svyglm(formula = Q13 ~ ppagecat + PPEDUCAT + income + PPREG4 + work,
       design = svy_never_some,
       family = quasibinomial(link = "logit"))
print_svy_mod(ns_demo)
```
## Some+every vs. never
```{r}
nse_demo <- svyglm(formula = Q13 ~ ppagecat + PPEDUCAT + income + PPREG4 + work,
       design = svy_never_someevery,
       family = quasibinomial(link = "logit"))
print_svy_mod(nse_demo)
```

# Demographic model + Belief (Q20)
Demographics + Q13 + Q20

## Every vs. never
```{r}
ne_demo_belief <- svyglm(formula = Q13 ~ ppagecat + PPEDUCAT + income + PPREG4 + work + Q20,
       design = svy_never_every,
       family = quasibinomial(link = "logit"))
print_svy_mod(ne_demo_belief)
```

## Some vs. never
```{r}
ns_demo_belief <- svyglm(formula = Q13 ~ ppagecat + PPEDUCAT + income + PPREG4 + work + Q20,
       design = svy_never_some,
       family = quasibinomial(link = "logit"))
print_svy_mod(ns_demo_belief)
```

## Some+every vs. never
```{r}
nse_demo_belief <- svyglm(formula = Q13 ~ ppagecat + PPEDUCAT + income + PPREG4 + work + Q20,
       design = svy_never_someevery,
       family = quasibinomial(link = "logit"))
print_svy_mod(nse_demo_belief)
```

### F statistic

```{r}
anova(ne_demo, ne_demo_belief, test = 'F')
```

```{r}
anova(ns_demo, ns_demo_belief, test = 'F')
```

```{r}
anova(nse_demo, nse_demo_belief, test = 'F')
```

### AIC/BIC

```{r}
AIC(ne_demo, ne_demo_belief)
AIC(ns_demo, ns_demo_belief)
AIC(nse_demo, nse_demo_belief)
```

```{r}
BIC(ne_demo, ne_demo_belief, maximal = ne_demo_belief)
BIC(ns_demo, ns_demo_belief, maximal = ns_demo_belief)
BIC(nse_demo, nse_demo_belief, maximal = nse_demo_belief)
```

Keep the belief variable.



# Social influence and herd immunity (Q15 + Q16 + Q17)

## Every vs. some
### Q15, Q16, Q17
```{r}
se_demo_belief_social <- svyglm(formula = Q13 ~ ppagecat + PPEDUCAT + income + PPREG4 + work + Q20 + Q15 + Q16 + Q17,
       design = svy_some_every,
       family = quasibinomial(link = "logit"))
print_svy_mod(se_demo_belief_social)
```

### F statistic

```{r}
#anova(ne_demo_belief_social, ne_demo_belief, test = 'F')
```
```{r}
#anova(ns_demo_belief_social, ns_demo_belief, test = 'F')
```
```{r}
#anova(nse_demo_belief_social, nse_demo_belief, test = 'F')
```

### AIC/BIC

```{r}
#AIC(ne_demo, ne_demo_belief, ne_demo_belief_social)
#AIC(ns_demo, ns_demo_belief, ns_demo_belief_social)
AIC(nse_demo, nse_demo_belief, se_demo_belief_social)
```

```{r}
#BIC(ne_demo, ne_demo_belief, ne_demo_belief_social, maximal = ne_demo_belief_social)
#BIC(ns_demo, ns_demo_belief, ns_demo_belief_social, maximal = ns_demo_belief_social)
BIC(nse_demo, nse_demo_belief, se_demo_belief_social, maximal = se_demo_belief_social)
```



# Social influence and herd immunity Sub
- Drop Q15

## Every vs. some
### Q16
```{r}
se_demo_belief_social <- svyglm(formula = Q13 ~ ppagecat + PPEDUCAT + income + PPREG4 + work + Q20 + Q16,
       design = svy_some_every,
       family = quasibinomial(link = "logit"))
print_svy_mod(se_demo_belief_social)
```

### Q16 + Q17
```{r}
se_demo_belief_social <- svyglm(formula = Q13 ~ ppagecat + PPEDUCAT + income + PPREG4 + work + Q20 + Q16 + Q17,
       design = svy_some_every,
       family = quasibinomial(link = "logit"))
print_svy_mod(se_demo_belief_social)
```


# Cost and health insurance (Q14, Q19, Q21)
- Run Q19 and Q21 separately

## Every vs. some
### Q14
```{r}
se_demo_belief_cost <- svyglm(formula = Q13 ~ ppagecat + PPEDUCAT + income + PPREG4 + work + Q20 + Q14,
       design = svy_some_every,
       family = quasibinomial(link = "logit"))
print_svy_mod(se_demo_belief_cost)
```

### Q19
```{r}
se_demo_belief_cost <- svyglm(formula = Q13 ~ ppagecat + PPEDUCAT + income + PPREG4 + work + Q20 + Q19,
       design = svy_some_every,
       family = quasibinomial(link = "logit"))
print_svy_mod(se_demo_belief_cost)
```

### Q21
```{r}
se_demo_belief_cost <- svyglm(formula = Q13 ~ ppagecat + PPEDUCAT + income + PPREG4 + work + Q20 + Q21,
       design = svy_some_every,
       family = quasibinomial(link = "logit"))
print_svy_mod(se_demo_belief_cost)
```

### Q14 + Q19
```{r}
se_demo_belief_cost <- svyglm(formula = Q13 ~ ppagecat + PPEDUCAT + income + PPREG4 + work + Q20 + Q14 + Q19,
       design = svy_some_every,
       family = quasibinomial(link = "logit"))
print_svy_mod(se_demo_belief_cost)
```


### AIC/BIC

```{r}
#AIC(ne_demo, ne_demo_belief, ne_demo_belief_social, ne_demo_belief_cost)
#AIC(ns_demo, ns_demo_belief, ns_demo_belief_social, ns_demo_belief_cost)
#AIC(nse_demo, nse_demo_belief, nse_demo_belief_social, nse_demo_belief_cost)
```

```{r}
#BIC(ne_demo, ne_demo_belief, ne_demo_belief_cost, maximal = ne_demo_belief_cost)
#BIC(ns_demo, ns_demo_belief, ns_demo_belief_cost, maximal = ns_demo_belief_cost)
#BIC(nse_demo, nse_demo_belief, nse_demo_belief_cost, maximal = nse_demo_belief_cost)
```


### Q13, Q20, Q16, Q17, Q14, Q19

```{r}
se_model <- svyglm(formula = Q13 ~ ppagecat + PPEDUCAT + income + PPREG4 + work + Q20 + Q16 + Q17 + Q14 + Q19,
       design = svy_some_every,
       family = quasibinomial(link = "logit"))
print_svy_mod(se_model)
```




# Barriers: Reasons to **not** get a vaccine
- Flip the response and Q18 variables

```{r}
library(forcats)
df <- readRDS('flu-survey/data/subset_recode.RDS')
never_some_flipped <- df[df$Q13 %in% c('Yes, some years', 'No, never'), ]
never_some_flipped$Q13 <- droplevels(never_some$Q13)
never_some_flipped$Q13 <- fct_relevel(never_some$Q13, 'Yes, some years', after = 0L)
table(never_some_flipped$Q13, useNA = 'always')
levels(never_some_flipped$Q13)

testthat::expect_equal(levels(never_some_flipped$Q13)[1], "Yes, some years")
```

```{r}
table(never_some_flipped$Q13, never_some_flipped$Q18_1, useNA = 'always')
```


```{r}
make_no_ref <- function(dat) {
  dat <- fct_relevel(dat, "No", after = 0L)
  testthat::expect_equal(levels(dat)[1], "No")
  return(dat)
}
```


```{r}
never_some_flipped$Q18_1 <- sapply(never_some_flipped$Q18_1, make_no_ref)
never_some_flipped$Q18_2 <- sapply(never_some_flipped$Q18_2, make_no_ref)
never_some_flipped$Q18_3 <- sapply(never_some_flipped$Q18_3, make_no_ref)
never_some_flipped$Q18_4 <- sapply(never_some_flipped$Q18_4, make_no_ref)
never_some_flipped$Q18_5 <- sapply(never_some_flipped$Q18_5, make_no_ref)
never_some_flipped$Q18_6 <- sapply(never_some_flipped$Q18_6, make_no_ref)
never_some_flipped$Q18_7 <- sapply(never_some_flipped$Q18_7, make_no_ref)
never_some_flipped$Q18_8 <- sapply(never_some_flipped$Q18_8, make_no_ref)
never_some_flipped$Q18_9 <- sapply(never_some_flipped$Q18_9, make_no_ref)
never_some_flipped$Q18_10 <- sapply(never_some_flipped$Q18_10, make_no_ref)

svy_never_some_flipped <- svydesign(ids = ~1, weights = ~weight, data = never_some_flipped[!is.na(never_some_flipped$weight), ])
```

```{r}
lapply(never_some_flipped[, 37:46], table)
```

```{r}
table(df$Q18_1, df$Q13)
```

- The reference response is "Yes, Some years."
- The model is modeling NOT getting a vaccine.

## Never vs. some
### Q18: 1-9
- p-value < 0.05 for Q18: 1, 2, 3, 5, 8
```{r}
ns_demo_belief_barriers <- svyglm(formula = Q13 ~ ppagecat + PPEDUCAT + income + PPREG4 + work + Q20 + Q18_1 + Q18_2 + Q18_3 + Q18_4 + Q18_5 + Q18_6 + Q18_7 + Q18_8 + Q18_9,
       design = svy_never_some_flipped,
       family = quasibinomial(link = "logit"))
print_svy_mod(ns_demo_belief_barriers)
```

```{r}
#ns_demo_belief_barriers <- svyglm(formula = Q13 ~ ppagecat + PPEDUCAT + income + PPREG4 + work + Q20 + Q18_1 + Q18_2 + #Q18_3 + Q18_4 + Q18_5 + Q18_6 + Q18_7 + Q18_8 + Q18_9 + Q18_10 + PPEDUCAT*Q20,
#       design = svy_never_some_flipped,
#       family = quasibinomial(link = "logit"))
#print_svy_mod(ns_demo_belief_barriers)
```


### Q18 + Q19
```{r}
ns_demo_belief_barriers <- svyglm(formula = Q13 ~ ppagecat + PPEDUCAT + income + PPREG4 + work + Q20 + Q18_1 + Q18_2 + Q18_3 + Q18_5 + Q18_7 + Q18_8 + Q19,
       design = svy_never_some_flipped,
       family = quasibinomial(link = "logit"))
print_svy_mod(ns_demo_belief_barriers)
```