---
title: "flu-all"
output:
  html_document:
    css: reports/style.css
    fig_height: 3
    fig_width: 6
    highlight: tango
    keep_md: yes
    theme: cosmo
    toc: yes
---

# Unweighted survey data

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T, warning = F, message = F, tidy = F, size = "small")
rm(list = ls(all.names = TRUE))

library(dplyr); library(tidyr); library(ggplot2)
library(knitr); library(gmodels); library(prettyR); library(epitools)
load("clean/cleaning2.RData")
load("clean/plotting1.RData")

data <- data2
names(data) <- old_name
names(data2) <- new_name
```

## Q1. Before receiving this survey, did you know influenza is different from the stomach flu?

### Ways to make tables

```{r Q1}
## Q1 table by gender

kable(with(data2, addmargins(table(PPGENDER, Q1))))  # formatted table

# using epitools::odds ratio with males as ref
(or <- oddsratio(with(data2, table(PPGENDER, Q2)), rev = "columns"))  # not sick, sick

# xtab gives OR (need to flip columns) and proportions
xtab(PPGENDER ~ Q1, data2)

# CrossTable gives pretty joint freqs, conditional %, marginal prop
with(data2, CrossTable(PPGENDER, Q1, prop.chisq = F))

# plot
g1 + geom_bar(mapping = aes(x = Q1, fill = Q1),
              position = position_dodge()) + facet_wrap(~PPGENDER)
```

#### by demographic variables

```{r}
## by age group
(or <- oddsratio(with(data2, table(ppagecat, Q1)), rev = "columns"))

## by education
(or1 <- oddsratio(with(data2, table(PPEDUCAT, Q1)), rev = "columns"))

g1 + geom_bar(mapping = aes(x = PPEDUCAT, fill = Q1),
              position = position_stack())
g1 + geom_bar(mapping = aes(x = PPEDUCAT, fill = Q1),
              position = position_fill()) 

## ETHNICITY
(or2 <- oddsratio(with(data2, table(PPETHM, Q1)), rev = "columns"))
g1 + geom_bar(mapping = aes(x = PPETHM, fill = Q1),
              position = position_dodge())

## INCOME
(or3 <- oddsratio(with(data2, table(PPINCIMP, Q1)), rev = "columns"))
g1 + geom_bar(mapping = aes(x = PPINCIMP, fill = Q1),
              position = position_dodge()) + coord_flip()

```


## Q2. Have you had an illness with influenza-like symptoms since August 2015?


```{r Q2}

## PPGENDER
xtab(PPGENDER ~ Q2, data2)
# facet plot
g2 + geom_bar(mapping = aes(x = Q2, fill = Q2), position = position_dodge()) + facet_wrap(~PPGENDER)


## PPETHM
xtab(PPETHM ~ Q2, data2)
g2 + geom_bar(mapping = aes(x = Q2, fill = PPETHM), position = position_dodge())


## PPINCIMP
xtab(PPINCIMP ~ Q2, data2)
g2 + geom_bar(mapping = aes(x = Q2, fill = PPINCIMP), position = position_dodge())

```


## Q3. Has any other person in your household had an illness with influenza like symptoms since August 2015?


```{r Q3}
with(data2, table(Q3))

# plot
g3 + geom_bar(mapping = aes(x = Q3, fill = Q3))


# PPGENDER
with(data2, table(PPGENDER, Q3))
# plot with facet
g3 + geom_bar(mapping = aes(x = Q3, fill = Q3), position = position_dodge()) + facet_wrap(~PPGENDER)

# PPETHM
with(data2, table(PPETHM, Q3))
# plot
g3 + geom_bar(mapping = aes(x = Q3, fill = PPETHM), position = position_dodge())

# PPINCIMP
with(data2, table(PPINCIMP, Q3))
# plot
g3 + geom_bar(mapping = aes(x = Q3, fill = PPINCIMP), position = position_dodge())
```


## Q4. Does your job require you to have a lot of contact with the public?


```{r Q4}
# + theme(axis.text.x = element_text(angle = 45, hjust = 1))
with(data2, table(Q4))

# plot
g4 + geom_bar(mapping = aes(x = Q4, fill = Q4))


# PPGENDER
with(data2, table(PPGENDER, Q4))
# plot with facet
g4 + geom_bar(mapping = aes(x = Q4, fill = Q4), position = position_dodge()) + facet_wrap(~PPGENDER)

# PPETHM
with(data2, table(PPETHM, Q4))
# plot
g4 + geom_bar(mapping = aes(x = Q4, fill = PPETHM), position = position_dodge())

# PPINCIMP
with(data2, table(PPINCIMP, Q4))
# plot
g4 + geom_bar(mapping = aes(x = Q4, fill = PPINCIMP), position = position_dodge())

```


## Q5. Do you have a car that you can use to travel to work?


```{r Q5}
with(data2, table(Q5))

# plot
g5 + geom_bar(mapping = aes(x = Q5, fill = Q5))


# PPGENDER
with(data2, table(PPGENDER, Q5))
# plot with facet
g5 + geom_bar(mapping = aes(x = Q5, fill = Q5), position = position_dodge()) + facet_wrap(~PPGENDER)

# PPETHM
with(data2, table(PPETHM, Q5))
# plot
g5 + geom_bar(mapping = aes(x = Q5, fill = PPETHM), position = position_dodge())

# PPINCIMP
with(data2, table(PPINCIMP, Q5))
# plot
g5 + geom_bar(mapping = aes(x = Q5, fill = PPINCIMP), position = position_dodge())
```


## Q6. Do you regularly use public transportation?


```{r}
with(data2, table(Q6))

# plot g6 <- ggplot(data2[!is.na(data2$Q6), ])
g6 + geom_bar(mapping = aes(x = Q6, fill = Q6))


# PPGENDER
with(data2, table(PPGENDER, Q6))
# plot with facet
g6 + geom_bar(mapping = aes(x = Q6, fill = Q6), position = position_dodge()) + facet_wrap(~PPGENDER)

# PPETHM
with(data2, table(PPETHM, Q6))
# plot
g6 + geom_bar(mapping = aes(x = Q6, fill = PPETHM), position = position_dodge())

# PPINCIMP
with(data2, table(PPINCIMP, Q6))
# plot
g6 + geom_bar(mapping = aes(x = Q6, fill = PPINCIMP), position = position_dodge())
```


## Q7. What types of public transportation do you regularly use?


```{r}
# make long data
q7_long <- data2 %>%
  gather(Q7_q, Q7_r, Q7_1_Bus:Q7_7_Other) %>%
    summarise(n = count())

with(q7_long, table(Q7_q, Q7_r))

q7_long %>%
  group_by(Q7_q, Q7_r, PPGENDER, PPETHM, PPINCIMP, ppagecat) %>%
  summarise(n = count())

# flip coordinates
ggplot(q7[!is.na(q7$Q7_r), ], aes(x = Q7_r, y = n, fill = Q7_r)) +
  geom_bar(stat = 'identity', position = position_dodge()) + facet_wrap(~Q7_q) + coord_flip()

# testing plot
ggplot(q7[!is.na(q7$Q7_r), ], aes(x = Q7_r, y = n, fill = Q7_r)) +
  geom_bar(stat = 'identity') +
  facet_grid(Q7_q ~ PPGENDER)


# by gender
with(q7_long, table(PPGENDER, Q7_q, Q7_r))

ggplot(q7[!is.na(q7$Q7_r), ], aes(x = Q7_r, y = n, fill = PPGENDER)) +
  geom_bar(stat = 'identity', position = position_dodge()) + facet_wrap(~Q7_q)

# by ethnicity
with(q7_long, table(PPETHM, Q7_q, Q7_r))

ggplot(q7[!is.na(q7$Q7_r), ], aes(x = Q7_r, y = n, fill = PPETHM)) +
  geom_bar(stat = 'identity', position = position_dodge()) + facet_wrap(~Q7_q)

# by income
with(q7_long, table(PPINCIMP, Q7_q, Q7_r ))

ggplot(q7[!is.na(q7$Q7_r), ], aes(x = Q7_r, y = n, fill = PPINCIMP)) +
  geom_bar(stat = 'identity', position = position_dodge()) + facet_wrap(~Q7_q)


```


## Q8. For what types of activities do you regularly use public transportation?


```{r}
q8_long <- data2 %>%
  gather("Q8_q", "Q8_r", starts_with("Q8_"), -contains("otherText"), -contains("Refused"))

with(q8_long, table(Q8_q, Q8_r))
q8 <- q8_long %>%
  count(Q8_q, Q8_r)


# PPGENDER
with(q8_long, table(PPGENDER, Q8_q, Q8_r))
q8 <- q8_long %>%
  group_by(PPGENDER, Q8_q, Q8_r) %>%
  count(PPGENDER, Q8_q, Q8_r)

# PPETHM
with(q8_long, table(PPETHM, Q8_q, Q8_r))


# PPINCIMP
with(q8_long, table(PPINCIMP, Q8_q, Q8_r))

```


## Q9. Do other members of your household regularly use public transportation?


```{r}
with(data2, table(Q9))

```


## Q10. What types of public transportation do other members of your household regularly use?


```{r}
#Q10 <- data2 %>%
#  select(CaseID, PPGENDER, PPAGE, PPEDUC, PPETHM, PPINCIMP, PPWORK, #Q10_1_Bus:Q10_9_Refused) %>%
#  gather("Q10_q", "Q10_r", Q10_1_Bus:Q10_8_Other)


q10_long <- data2 %>%
  gather("Q10_q", "Q10_r", starts_with("Q10_"), -contains("Text"), -contains("Refused"), na.rm = TRUE)

with(q10_long, table(Q10_q, Q10_r))
q10 <- q10_long %>%
  count(Q10_q, Q10_r)


# PPGENDER
with(q10_long, table(PPGENDER, Q10_q, Q10_r))
q10 <- q10_long %>%
  group_by(PPGENDER, Q10_q, Q10_r) %>%
  count(PPGENDER, Q10_q, Q10_r)

# PPETHM
with(q10_long, table(PPETHM, Q10_q, Q10_r))


# PPINCIMP
with(q10_long, table(PPINCIMP, Q10_q, Q10_r))

```


### Q11. How do you rate your risk of getting influenza if you visited each of the following locations?


```{r}
q11_long <- data2 %>%
  gather("Q11_q", "Q11_r", starts_with("Q11_"), -contains("Text"), -contains("Refused"), na.rm = TRUE)


with(q11_long, table(Q11_q, Q11_r))
q11 <- q11_long %>%
  count(Q11_q, Q11_r)

ggplot(q11[!is.na(q11$Q11_r), ], aes(x = Q11_r, y = n, fill = Q11_r)) +
  geom_bar(stat = 'identity', position = position_dodge()) + facet_wrap(~Q11_q) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

# by gender
with(q11_long, table(PPGENDER, Q11_r, Q11_q))
q11 <- q11_long %>%
  group_by(PPGENDER, Q11_q, Q11_r) %>%
  count(PPGENDER, Q11_q, Q11_r)

ggplot(q11[!is.na(q11$Q11_r), ], aes(x = Q11_r, y = n, fill = PPGENDER)) +
  geom_bar(stat = 'identity', position = position_dodge()) + facet_wrap(~Q11_q) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))


# by ethnicity
with(q11_long, table(PPETHM, Q11_r, Q11_q))
q11 <- q11_long %>%
  group_by(PPETHM, Q11_q, Q11_r) %>%
  count(PPETHM, Q11_q, Q11_r)

ggplot(q11[!is.na(q11$Q11_r), ], aes(x = Q11_r, y = n, fill = PPETHM)) +
  geom_bar(stat = 'identity', position = position_dodge()) + facet_wrap(~Q11_q) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))


# by income
with(q11_long, table(PPINCIMP, Q11_q, Q11_r))
q11 <- q11_long %>%
  group_by(PPINCIMP, Q11_q, Q11_r) %>%
  count(PPINCIMP, Q11_q, Q11_r)

ggplot(q11[!is.na(q11$Q11_r), ], aes(x = Q11_r, y = n, fill = PPINCIMP)) +
  geom_bar(stat = 'identity', position = position_dodge()) + facet_wrap(~Q11_q) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```



### Q12. Which of the following actions do you take to avoid getting sick?

```{r}
Q12 <- data2 %>%
  select(PPGENDER, PPAGE, PPEDUC, PPETHM, PPINCIMP, PPWORK, 75:91) %>%
  gather("q", "r", 7:21)

with(Q12, table(q, r))
q12 <- Q12 %>%
  count(q, r)

```

### Q13. Do you get the flu vaccine?

```{r}
with(data2, table(Q13))
ggplot(data2[!is.na(data2$Q13), ]) + geom_bar(mapping = aes(x = Q13, fill = Q13), position = position_dodge())


# by gender
with(data2, table(Q13, PPGENDER))
q13 <- data2 %>%
  count(Q13, PPGENDER)

ggplot(q13[!is.na(q13$Q13), ], aes(x = Q13, y = n, fill = PPGENDER)) +
  geom_bar(stat = 'identity', position = position_dodge())


# by eth
with(data2, table(Q13, PPINCIMP))
q13 <- data2 %>%
  count(Q13, PPINCIMP)

ggplot(q13[!is.na(q13$Q13), ], aes(x = Q13, y = n, fill = PPINCIMP)) +
  geom_bar(stat = 'identity', position = position_dodge())


```


### Q14. How much do you pay to get an influenza vaccine?

```{r}
with(data2, table(Q14))
ggplot(data2[!is.na(data2$Q14), ]) + geom_bar(mapping = aes(x = Q14, fill = Q14), position = position_dodge())


# by gender
with(data2, by(Q14, PPGENDER, summary))

```

### Q15. Are you more likely to get a vaccine if others around you get a vaccine?
```{r}
with(data2, table(Q15))

ggplot(data2[!is.na(data2$Q15), ]) + geom_bar(mapping = aes(x = Q15, fill = Q15), position = position_dodge())

#
with(data2, table(Q15, PPGENDER))
#
with(data2, table(Q15, PPETHM))
#
with(data2, table(PPINCIMP, Q15))
```

### Q16. Are you more likely to get a vaccine if others around you do not get a vaccine?

```{r}
with(data2, table(Q16))
ggplot(data2[!is.na(data2$Q16), ]) + geom_bar(mapping = aes(x = Q16, fill = Q16), position = position_dodge())

#
with(data2, table(Q16, PPGENDER))
#
with(data2, table(Q16, PPETHM))
#
with(data2, table(PPINCIMP, Q16))

```

### Q17. Do you get a vaccine to protect yourself, protect others, or protect yourself and others?

```{r}
with(data2, table(Q17))
ggplot(data2[!is.na(data2$Q17), ]) + geom_bar(mapping = aes(x = Q17, fill = Q17), position = position_dodge())

#
with(data2, table(Q17, PPGENDER))
#
with(data2, table(Q17, PPETHM))
#
with(data2, table(PPINCIMP, Q17))

```



### Q18. What are the reasons you would not get an influenza vaccine?

```{r}
Q18 <- data2 %>%
  select(PPGENDER, PPAGE, PPEDUC, PPETHM, PPINCIMP, PPWORK, 97:108) %>%
  gather("q", "r", 7:Q18_10_Other)

with(Q18, table(q, r))
q18 <- Q18 %>%
  count(q, r)
```

### Q19. Do you have health insurance?

```{r}
with(data2, table(Q19))
ggplot(data2[!is.na(data2$Q19), ]) + geom_bar(mapping = aes(x = Q19, fill = Q19), position = position_dodge())

#
with(data2, table(Q19, PPGENDER))
#
with(data2, table(Q19, PPETHM))
#
with(data2, table(PPINCIMP, Q19))
```

### Q20. How effective do you think the influenza vaccine is in protecting people from becoming sick with influenza?

```{r}
with(data2, table(Q20))
ggplot(data2[!is.na(data2$Q20), ]) + geom_bar(mapping = aes(x = Q20, fill = Q20), position = position_dodge())


#
with(data2, table(Q20, PPGENDER))
#
with(data2, table(Q20, PPETHM))
#
with(data2, table(PPINCIMP, Q20))

```

### Q21. Are influenza vaccines covered by your health insurance?

```{r}
with(data2, table(Q21))
ggplot(data2[!is.na(data2$Q21), ]) + geom_bar(mapping = aes(x = Q21, fill = Q21), position = position_dodge())

#
with(data2, table(Q21, PPGENDER))
#
with(data2, table(Q21, PPETHM))
#
with(data2, table(PPINCIMP, Q21))

```

### Q22. Do you do any of the following when you have influenza symptoms?

```{r}
Q22 <- data2 %>%
  select(PPGENDER, PPAGE, PPEDUC, PPETHM, PPINCIMP, PPWORK, 112:122) %>%
  gather("q", "r", 7:Q22_9_Other)

with(Q22, table(q, r))
q22 <- Q22 %>%
  count(q, r)

```

### Q23. Which of the following actions do you take when you have influenza symptoms to avoid someone else from getting sick?

```{r}
Q23 <- data2 %>%
  select(PPGENDER, PPAGE, PPEDUC, PPETHM, PPINCIMP, PPWORK, 123:Q23_11_Other) %>%
  gather("q", "r", 7:Q23_11_Other)

with(Q23, table(q, r))
q23 <- Q23 %>%
  count(q, r)

```

### Q24. What sources of information do you recall hearing or seeing about influenza outbreaks? 

```{r}
Q24 <- data2 %>%
  select(PPGENDER, PPAGE, PPEDUC, PPETHM, PPINCIMP, PPWORK, 137:Q24_7_Refused) %>%
  gather("q", "r", 7:Q24_6_Other)

with(Q24, table(q, r))
q24 <- Q24 %>%
  count(q, r)
```

### Q25. If you received information from the news, internet or other public media that there was an influenza outbreak in your community would you do any of the following?

```{r}
Q25 <- data2 %>%
  select(PPGENDER, PPAGE, PPEDUC, PPETHM, PPINCIMP, PPWORK, 145:Q25_11_Other) %>%
  gather("q", "r", 7:Q25_11_Other)

with(Q25, table(q, r))
q25 <- Q25 %>%
  count(q, r)

```

### Q26. Does your household have children?

```{r}
with(data2, table(Q26))
ggplot(data2[!is.na(data2$Q26), ]) + geom_bar(mapping = aes(x = Q26, fill = Q26), position = position_dodge())

```

### Q27. What actions do you take when a child in your household has influenza symptoms?

```{r}
Q27 <- data2 %>%
  select(PPGENDER, PPAGE, PPEDUC, PPETHM, PPINCIMP, PPWORK, 159:Q27_4_Other) %>%
  gather("q", "r", 7:Q27_4_Other)

with(Q27, table(q, r))
q27 <- Q27 %>%
  count(q, r)
```

### Q28. Are you a single parent?

```{r}
with(data2, table(Q28))
ggplot(data2[!is.na(data2$Q28), ]) + geom_bar(mapping = aes(x = Q28, fill = Q28), position = position_dodge())

```

### Q29. How do you care for a sick child?

```{r}
Q29 <- data2 %>%
  select(PPGENDER, PPAGE, PPEDUC, PPETHM, PPINCIMP, PPWORK, 166:Q29_6_Other) %>%
  gather("q", "r", 7:Q29_6_Other)

with(Q29, table(q, r))
q29 <- Q29 %>%
  count(q, r)
```

### Q30. How do you care for a sick child?

```{r}
Q30 <- data2 %>%
  select(PPGENDER, PPAGE, PPEDUC, PPETHM, PPINCIMP, PPWORK, 174:Q30_6_Other) %>%
  gather("q", "r", 7:Q30_6_Other)

with(Q30, table(q, r))
q30 <- Q30 %>%
  count(q, r)

```

### Q31. How many hours of screen time (time spent watching television, a computer, smartphone, iPad, etc.) do you spend each day on average when you are not sick? Enter 0 if none

```{r}
with(data2, summary(Q31))

# by gender
with(data2, by(Q31, PPGENDER, summary))
#
with(data2, by(Q31, PPETHM, summary))
#
with(data2, by(Q31, PPINCIMP, summary))

```

### Q32. How many hours of screen time do you spend each day on average when you are sick? Enter 0 if none

```{r}
with(data2, summary(Q32))

# by gender
with(data2, by(Q32, PPGENDER, summary))
#
with(data2, by(Q32, PPETHM, summary))
#
with(data2, by(Q32, PPINCIMP, summary))

```

### Q33. How many people, including yourself, reside in your household?

```{r}
with(data2, summary(Q33))

# by gender
with(data2, by(Q33, PPGENDER, summary))
#
with(data2, by(Q31, PPETHM, summary))
#
with(data2, by(Q31, PPINCIMP, summary))

```


