---
title: "Bivariate and multivariate analyses"
output: 
  html_document:
    fig_height: 3
    fig_width: 6
    highlight: default
    keep_md: yes
    theme: cosmo
    toc: yes
    toc_depth: 2
---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T, warning = F, message = F, tidy = F, size = "small")
rm(list = ls(all.names = TRUE))
library(rmarkdown)
library(dplyr); library(tidyr); library(ggplot2)
library(survey); library(car); library(memisc)
#library(mosaic)
#trellis.par.set(theme=theme.mosaic()) # change default color scheme for lattice
```

```{r load-data}
## Load data and recoded variables.

load("~/git/flu-survey/data/cleaning2.RData")
data <- dataf

#source(recoding.R)
load("~/git/flu-survey/data/recoding.RData")
df <- datar  # datar contains recoded variables
#tail(df)
```

```{r survey-object}
## Create survey object with weights, des

options(digits = 4)
options(survey.lonely.psu = "adjust")
des <- svydesign(ids = ~1, weights = ~weight, data = data[is.na(data$weight) == F, ])
#summary(des)
```

# Survey questions

## Q1. Before receiving this survey, did you know influenza is different from the stomach flu?
  
### Compare sex ratios in unweighted and weighted data frames for Q1.

```{r q1}
# unweighted Q1
with(data, addmargins(table(Q1, PPGENDER)))
# weighted Q1
svytable(~Q1 + PPGENDER, design = des, round = T)

# another unweighted table
svyby(~Q1, ~Q1+PPGENDER, des, unwtd.count)

# unweighted prop
(u <- with(data, prop.table(table(Q1, PPGENDER), margin = 2))*100)  
# weighted prop
(w <- prop.table(svytable(~Q1 + PPGENDER, design = des), margin = 2)*100)

# figure out how to plot weighted survey designs

# table above with standard errors
svyby(formula = ~Q1, by = ~PPGENDER, design = des, FUN = svymean, na.rm = T)
```

In the unweighted data frame, `r u[1]`% of females and `r u[3]`% of males answered Yes. `r u[4]`% of males and `r u[2]`% of females answered No.  
In the weighted data frame, `r w[1]`% of females and `r w[3]`% of males answered Yes. `r w[4]`% of males and `r w[2]`% of females answered No.  
  

## Q2. Have you had an illness with influenza-like symptoms since August 2015?

### First look at unweighted data. Calculate unadjusted OR for being sick by gender.

```{r q2}
## without weights

# recode datar$Q2
head(datar$Q2)
df$sick <- car::recode(datar$Q2, recodes = "'Yes' = 1; 'No' = 0; NA = NA")
head(df$sick)

# table Q2 by gender
with(df, table(Q2, PPGENDER))

# glm without weights
fit1 <- glm(sick ~ PPGENDER, data = df, family = binomial())
summary(fit1)
(q2.u <- exp(coefficients(fit1)))  # OR
```

The unadjusted odds ratio of being sick as a male is `r q2.u[2]` compared to females.


### Apply survey design and weights for Q2. Calculate unadjusted OR for getting sick by gender.

```{r}
## With survey weights

# relevel PPGENDER
df$PPGENDER <- relevel(datar$PPGENDER, "Male")

# create updated survey object with weights = des2
options(survey.lonely.psu = "adjust")
des2 <- svydesign(ids = ~1, weights = ~weight, data = df)  # data = df

# svyglm with weighted model
m1 <- svyglm(sick ~ PPGENDER, des2, family = quasibinomial())
summary(m1)
(or1 <- exp(coefficients(m1)))  # unadjusted OR
exp(confint(m1))  # 95% CI 
```

In the weighted data frame, females had `r or1[2]` times the odds of being sick compared to males.

### Calculate OR for being sick, adjusted for ethnicity

```{r}
# being sick, by ethnicity
m2 <- svyglm(sick ~ PPETHM, des2, family = quasibinomial())
summary(m2)
(or2 <- exp(coefficients(m2)))  # OR adjusted for race
exp(confint(m2))  # note 95% CI for hispanic group
```

Compared to whites, OR for being sick are `r or2[2:5]` for blacks, hispanics, others, and 2+ races, respectively.  
  
Notes: When a logistic regression is calculated, the regression coefficient (b1) is the estimated increase in the log odds of the outcome per unit increase in the value of the exposure; the exponential function of the regression coefficient (e^b1) is the odds ratio associated with a one-unit increase in the exposure.  
  
```{r, eval=FALSE, include=FALSE}
########## do not run ############

## same as above but with recoded 1,0 variables; can change reference variable to remove (e.g. white)
# first recode xi variables
summary(datar$PPETHM)
df$white <- car::recode(datar$PPETHM, recodes = "'White, Non-Hispanic' = 1; NA = NA; else = 0")
df$black <- car::recode(datar$PPETHM, recodes = "'Black, Non-Hispanic' = 1; NA = NA; else = 0")
df$hispanic <- car::recode(datar$PPETHM, recodes = "'Hispanic' = 1; NA = NA; else = 0")
df$otherrace <- car::recode(datar$PPETHM, recodes = "'Other, Non-Hispanic' = 1; NA = NA; else = 0")
df$more2race <- car::recode(datar$PPETHM, recodes = "'2+ Races, Non-Hispanic' = 1; NA = NA; else = 0")
tail(df)

# create survey design mx
options(survey.lonely.psu = "adjust")
desx <- svydesign(ids = ~1, weights = ~weight, data = df)  # data = df
mx <- svyglm(sick ~ black+hispanic+otherrace+mixedrace, desx, family = quasibinomial())  # white is reference?
summary(mx)
(orx <- exp(coefficients(mx)))  # odds ratios
```

***

### Compare model variables for being sick.

```{r}
#des2 <- svydesign(ids = ~1, weights = ~weight, data = df)

## sick = 1, not sick = 0
# add variables to glm with survey design
a1 <- svyglm(sick ~ PPGENDER, des2, family = quasibinomial())  # by gender
a2 <- update(a1, ~ . + PPETHM)  # adjust for race
a3 <- update(a2, ~ . + work)  #  work
a4 <- update(a3, ~ . + marital)  # marital status

# memisc: need to modify summary function
mtable(a1, a2, a3, a4)

# AOR for last glm
(or <- exp(coefficients(a4)))
```

When adjusting for gender, ethnicity, employment, and marital status, significant variables for being sick included female gender (OR = `r or[2]`) and hispanic ethnicity (OR = `r or[4]`)

***

## Q13. Do you get an influenza vaccine? (Yes, every year; Yes, some years; No, never)

```{r q13}
# first make sure Q13 has been re-grouped
head(datar$Q13)  # original
head(df$q13)  # updated

# relevel q13
df$q13 <- relevel(df$q13, "No")

# update survey object
options(survey.lonely.psu = "adjust")
des3 <- svydesign(ids = ~1, weights = ~weight, data = df)

# getting sick ~ getting vaccine
m5 <- svyglm(sick ~ q13, des3, family = quasibinomial)
summary(m5)
(or5 <- exp(coefficients(m5)))
```

Those who get the vaccine had `r or5[2]` the odds of getting sick compared to those who do not get the vaccine.

```{r}
# Q2 + Q13 tables with weights
svytable(~q13 + sick, design = des3, round = T)  # sick = 1, not sick = 0
(t2 <- prop.table(svytable(~q13 + sick, design = des2), margin = 2)* 100)
(t1 <- prop.table(svytable(~q13 + sick, design = des2), margin = 1)* 100)
```

Out of those who reported being sick, `r t2[4]`% reported receiving vaccine.  
Out of those who were healthy, `r t2[3]`% received vaccine (`r t2[1]`% did not).  
  
Vaccinated group: `r t1[3]`% report no illness.  
Unvaccinated group: `r t1[1]`% report no illness.  
  
***

### Logistic regression for Q2 and Q13. Subset sick + vaccinated group. 

```{r}
# subset sick and vaccinated into new df2
df2 <- df %>%
  mutate(sickq13 = ifelse((sick == 1 & q13 == "Yes"), 1, 0))

df2$sickq13 <- as.factor(df2$sickq13)
str(df2$sickq13)

# table of sick and vaccine status
xtabs(~sick + q13, df2)
# sick and vaccinated = 1, else = 0
table(df2$sickq13)
```

### Run regression and adjust for demographic variables.

```{r}
# update survey object
options(survey.lonely.psu = "adjust")
des4 <- svydesign(ids = ~1, weights = ~weight, data = df2)

m1 <- svyglm(sickq13 ~ PPGENDER, des4, family = quasibinomial())
m2 <- update(m1, ~ . + PPETHM)  # add race
m3 <- update(m2, ~ . + work)  # add work
m4 <- update(m3, ~ . + ppagecat)  # add age

# memisc, need to modify summary function
mtable(m1, m2, m3, m4)  # this isn't very helpful


# who is getting sick after vaccinations?
svyby(formula = ~ppagecat, by = ~sickq13, design = des4, FUN = svymean, na.rm = T)
svyby(formula = ~PPGENDER, by = ~sick + q13, design = des4, FUN = svymean, na.rm = T)
```


## in progress

```{r, eval=FALSE, include=FALSE}
## testing analysis ##

# update survey object
options(survey.lonely.psu = "adjust")
desx <- svydesign(ids = ~1, weights = ~weight, data = df2)

n0 <- svyglm(sick ~ Q11_1 + Q11_2 + Q11_3 + Q11_4 + Q11_5 + Q11_6 + Q11_7
             + Q11_8 + Q11_9 + Q11_10 + Q11_11, desx, family = quasibinomial())

summary(n0)
exp(coefficients(n0))


n1 <- svyglm(sick ~ q13, desx, family = quasibinomial())
n2 <- update(n1, ~ . + PPGENDER + PPETHM)
n3 <- update(n2, ~ . + ppagecat)
mtable(n1, n2, n3)
```

```{r, eval=FALSE, include=FALSE}
## testing analysis ##

svyglm(sick ~ q13, desx, family = quasibinomial())

o1 <- svyglm(sick ~ q13, desx, family = quasibinomial())
o2 <- update(o1, ~ . + PPGENDER + PPETHM)
o3 <- update(o2, ~ . + ppagecat)
o4 <- update(o3, ~ . + ppagecat)
mtable(o1, o2, o3)
```


