---
title: "Household members"
output:
  html_document:
    fig_caption: yes
    fig_height: 3
    fig_width: 6
    highlight: tango
    keep_md: yes
    theme: cosmo
    toc: yes
    toc_depth: 4
fontsize: 10pt
---

This report contains survey data analysis for household members.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T, warning = F, message = F, tidy = F, size = "small")
rm(list = ls(all.names = TRUE))

library(dplyr)
library(tidyr)
library(ggplot2)

load("~/git/flu-survey/data/cleaning2.RData")
```

All household members.

```{r}
data2 <- dat
names(dat[407:417])

# select respondent's education, race, income, location + household data
data_hhm1 <- data2 %>%
  select(c(PPEDUCAT, PPETHM, PPINCIMP, ppreg9, PPSTATEN, 374:375, 407:417)) %>%
  filter(!is.na(HHM1_AGE))

data_hhm2 <- data2 %>%
  select(c(PPEDUCAT, PPETHM, PPINCIMP, ppreg9, PPSTATEN, 405:406, 418:428)) %>%
  filter(!is.na(HHM2_AGE))

# all ages histogram
with(data_hhm1, hist(HHM1_AGE))
with(data_hhm2, hist(HHM2_AGE))

```

Household children.
- includes respondent's education, race, income, location
- join/merge hhm1 and hhm2 into single dataframe

```{r}
# subset children < age 18
child1 <- data_hhm1 %>%
  filter(HHM1_AGE < 18)
child2 <- data_hhm2 %>%
  filter(HHM2_AGE < 18)

# count total number of children <18 years
child1 %>%
  group_by(HHM1_AGE) %>%
  summarise(n = n()) %>%
  summarise(sum(n))
child2 %>%
  group_by(HHM2_AGE) %>%
  summarise(n = n()) %>%
  summarise(sum(n))

# append dataframes, rename columns to be the same
nam <- c("PPEDUCAT", "PPETHM", "PPINCIMP", "ppreg9", "PPSTATEN", "age", "name", "gender",
         "Q36", "Q36_Codes", "Q37", "Q37_Codes", "Q38", "Q38_Codes",
         "Q39", "Q40", "Q41", "Q42")
names(child1) <- nam
names(child2) <- nam

children <- rbind(child1, child2)

rm(data_hhm1, data_hhm2, child1, child2)
```

Total number of children = 270 + 260 = 530

```{r}
# age histogram
with(children, hist(age))
```




# Survey questions
### Q35. What is the gender of this member of the household?


```{r}
with(children, summary(gender))

```

### Q36. On average, how many days per week does this member of your household work or attend day care or school outside of your home?

```{r}
with(children, hist(Q36))
with(children, summary(Q36))

```

### Q37. On average, how many days per week does this member of your household participate in social activities outside of your home?

```{r}
with(children, hist(Q37))
with(children, summary(Q37))

```

### Q38. On average, how many days per week does this member of your household use public transportation?

```{r}
with(children, hist(Q38))
with(children, summary(Q38))

```

### Q39. How frequently does this member of your household visit a doctor's office for wellness appointments?

```{r}
with(children, summary(Q39))
with(children, barplot(table(Q39)))

```

### Q40. How frequently does this member of the household get sick in a typical year?

```{r}
with(children, summary(Q40))
with(children, barplot(table(Q40)))

```


### Q41. How many times has this member of your household had influenza or another respiratory illness in the last two years?


```{r}
with(children, summary(Q41))
with(children, barplot(table(Q41)))

```


### Q42. Does this member of your household get an annual influenza vaccine?


```{r}
with(children, summary(Q42))
with(children, barplot(table(Q42)))

# vaccine by age
with(children, table(age, Q42))

# regroup variables


```



