---
title: "Analysis"
author: "Daniel Chen"
date: "November 13, 2017"
output:
  html_document:
    df_print: kable
    number_sections: yes
    smart: no
    toc: yes
  pdf_document:
    toc: yes
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = '..')
```

```{r}
library(survey)
library(magrittr)
library(broom)

rm(list = ls())

```

```{r set-options, echo=FALSE, cache=FALSE}
options(width = 90)
```


```{r}
# recode values
recode_never_somealways <- function(value) {
  if (is.na(value)) {
    return(NA)
  } else if (value == 'No, never') {
    return(value)
  } else if (value %in% c('Yes, some years', 'Yes, every year')) {
    return('Yes, Sometimes or Always')
  } else {
    return(NA)
  }
}
```

```{r}
p_star <- function(pvalue) {
  if (pvalue <= .001) {
    return('***')
  } else if (pvalue <= .01) {
    return('**')
  } else if (pvalue <= .05) {
    return('*')
  } else {
    return('')
  }
}
```


```{r}
# get or results from logistic model
logistic_or <- function(mod) {
  mod_res <- tidy(mod)
  mod_res$or <- exp(mod_res$estimate)
  mod_res$or_std_err <- exp(mod_res$std.error)
  mod_res$or_lower <- mod_res$or - 1.96 * mod_res$or_std_err
  mod_res$or_upper <- mod_res$or + 1.96 * mod_res$or_std_err
  mod_res$term <- stringr::str_replace(mod_res$term, 'as.factor', '')
  
  mod_res$sig <- sapply(mod_res$p.value, p_star)
  
  mod_res <- mod_res %>%
    dplyr::select(term, or:sig, estimate:p.value)
  return(mod_res)
}
```

```{r}
fit_all_dat <- function(formula,
                        d1 = svy_never_every,
                        d2 = svy_never_sometimes,
                        d3 = svy_df) {
  
  for (d in list(d1, d2, d3)) {
    mod <- survey::svyglm(formula,
                          design = d,
                          family = quasibinomial(link = "logit"))
    print(summary(mod))
    mod_res <- logistic_or(mod)
    print(mod_res)
    print('********************************************************************')
  }
}
```


```{r}
# this file is created at the end of "analysis-draft.Rmd"
df <- readRDS('./data/data_for_models.RDS')

df$Q13 <- as.character(df$Q13)
df$Q1 <- as.character(df$Q1)
```

```{r}
names(df)
```



# Q13. Do you get the flu vaccine?

```{r}
table(df$Q13, useNA = 'always') %>%
  addmargins()
```

## Recode reponse variable

Three types of outcomes:

- Never/Every
- Never/Sometimes
- Never/SomeAlways

### Never and Every
```{r}
dim(df)
```


```{r}
never_every <- df[df$Q13 %in% c('Yes, every year', 'No, never'), ]
dim(never_every)
```

```{r}
table(never_every$Q13, useNA = 'always') %>%
  addmargins()
```

### Never and Sometimes

```{r}
never_sometimes <- df[df$Q13 %in% c('Yes, some years', 'No, never'), ]
dim(never_sometimes)
```

```{r}
table(never_sometimes$Q13, useNA = 'always') %>%
  addmargins()
```

### Never and Sometimes/Always

```{r}
dim(df)
```


```{r}
df$q13_never_somealways <- sapply(X = df$Q13, FUN = recode_never_somealways)
```

```{r}
dim(df)

testthat::expect_equal(dim(df), c(2168, 56))
```

```{r}
# check to make sure the recoding was correct
table(df$Q13, df$q13_never_somealways, useNA = 'always') %>%
  addmargins()
```


## Logistic Regression Models (Demographic Only)

```{r}
svy_never_every <- svydesign(ids = ~1, weights = ~weight,
                             data = never_every[!is.na(never_every$weight), ])
svy_never_sometimes <- svydesign(ids = ~1, weights = ~weight,
                                 data = never_sometimes[!is.na(never_sometimes$weight), ])
svy_df <- svydesign(ids = ~1, weights = ~weight,
                    data = df[!is.na(df$weight), ])
```


### Never vs Always

```{r}
# deomogrpahic variables
c("PPGENDER", "ppagect4", "PPEDUCAT", "PPETHM", "income", "marital", "PPMSACAT", "PPREG4", "work")
```


```{r}
# formula for all demographic variales
form_demo <- 'as.factor(Q13) ~ as.factor(PPGENDER) + as.factor(ppagect4) + as.factor(PPEDUCAT) + as.factor(PPETHM) + as.factor(income) + as.factor(marital) + as.factor(PPMSACAT) + as.factor(PPREG4) + as.factor(work)'
form_demo <- as.formula(form_demo)
```


```{r}
# unweighted glm
# mod <- glm(data = never_every,
#            formula = form,
#            family = binomial(link = "logit"),
#            na.action = 'na.omit')

# summary(mod)
# mod_res <- logistic_or(mod)
# mod_res
```

```{r}
# what happens if we just use regular binomial?
# mod <- survey::svyglm(form,
#                       design = svy_never_every,
#                       family = binomial(link = "logit"))
# summary(mod)
# mod_res <- logistic_or(mod)
# mod_res
```

```{r}
# documentation says to use qusibinomial
mod <- survey::svyglm(form_demo,
                      design = svy_never_every,
                      family = quasibinomial(link = "logit"))
summary(mod)
mod_res <- logistic_or(mod)
mod_res
```


### Never vs Sometimes

```{r}
mod <- survey::svyglm(form_demo,
                      design = svy_never_sometimes,
                      family = quasibinomial(link = "logit"))
summary(mod)
mod_res <- logistic_or(mod)
mod_res
```


### Never vs SomeAlways

```{r}
mod <- survey::svyglm(form_demo,
                      design = svy_df,
                      family = quasibinomial(link = "logit"))
summary(mod)
mod_res <- logistic_or(mod)
mod_res
```

## Full Logistic Regression Models (Demographic + Survey questions)

```{r}
form_demo_svy <- 'as.factor(Q13) ~ as.factor(PPGENDER) + as.factor(ppagect4) + as.factor(PPEDUCAT) + as.factor(PPETHM) + as.factor(income) + as.factor(marital) + as.factor(PPMSACAT) + as.factor(PPREG4) + as.factor(work) + as.factor(Q20) + as.factor(Q15) + as.factor(Q16) + as.factor(Q17) + as.factor(Q14) + as.factor(Q19)'
form_demo_svy <- as.formula(form_demo_svy)
```

### Never vs Always

```{r}
mod <- survey::svyglm(form_demo_svy,
                      design = svy_never_every,
                      family = quasibinomial(link = "logit"))
summary(mod)
mod_res <- logistic_or(mod)
mod_res
```

### Never vs SomeAlways

```{r}
mod <- survey::svyglm(form_demo_svy,
                      design = svy_never_sometimes,
                      family = quasibinomial(link = "logit"))
summary(mod)
mod_res <- logistic_or(mod)
mod_res
```

### Never vs Somealways

```{r}
mod <- survey::svyglm(form_demo_svy,
                      design = svy_df,
                      family = quasibinomial(link = "logit"))
summary(mod)
mod_res <- logistic_or(mod)
mod_res
```

## Logistic Regression (demo + Beliefs and perceptions)


```{r}
f <- as.formula('as.factor(Q13) ~ as.factor(PPGENDER) + as.factor(ppagect4) + as.factor(PPEDUCAT) + as.factor(PPETHM) + as.factor(income) + as.factor(marital) + as.factor(PPMSACAT) + as.factor(PPREG4) + as.factor(work) + as.factor(Q20)')
fit_all_dat(f)
```


## Logistic Regression (demo + Social influence and herd immunity)

```{r}
f <- as.formula('as.factor(Q13) ~ as.factor(PPGENDER) + as.factor(ppagect4) + as.factor(PPEDUCAT) + as.factor(PPETHM) + as.factor(income) + as.factor(marital) + as.factor(PPMSACAT) + as.factor(PPREG4) + as.factor(work) + as.factor(Q15) + as.factor(Q16) + as.factor(Q17)')
fit_all_dat(f)
```

## Logistic Regression (demo + Cost and health insurance)

```{r}
f <- as.formula('as.factor(Q13) ~ as.factor(PPGENDER) + as.factor(ppagect4) + as.factor(PPEDUCAT) + as.factor(PPETHM) + as.factor(income) + as.factor(marital) + as.factor(PPMSACAT) + as.factor(PPREG4) + as.factor(work) + as.factor(Q14) + as.factor(Q19)')
fit_all_dat(f)
```



formula for the full model (easier to copy/paste and edit)

`as.factor(Q13) ~ as.factor(PPGENDER) + as.factor(ppagect4) + as.factor(PPEDUCAT) + as.factor(PPETHM) + as.factor(income) + as.factor(marital) + as.factor(PPMSACAT) + as.factor(PPREG4) + as.factor(work) + as.factor(Q20) + as.factor(Q15) + as.factor(Q16) + as.factor(Q17) + as.factor(Q14) + as.factor(Q19)`
