---
title: "Analysis summary part 2"
output: 
  html_document:
    fig_caption: yes
    fig_height: 4
    fig_width: 6
    keep_md: yes
    toc: yes
    toc_depth: 2
---

## Q11. How do you rate your risk of getting influenza if you visited each of the following locations?
```{r}

```

## Q12. Which of the following actions do you take to avoid getting sick?
```{r}

```

## Q13. Do you get the flu vaccine?

```{r q13-plot}
q13 <- as.data.frame(svytable(
  ~Q13 + PPGENDER + ppagect4 + PPETHM + income + PPEDUCAT + work + marital, des, round = T))

p <- ggplot(q13, aes(Q13, weight = Freq)) + ptext
fil <- aes(fill = Q13)

p + geom_bar()
gen <- p + pgen + fil + geom_bar(position = "dodge")
age <- p + page + fil + geom_bar(position = "dodge")
eth <- p + peth + fil + geom_bar(position = "dodge") + coord_flip()
inc <- p + pinc + fil + geom_bar(position = "dodge")
edu <- p + pedu + fil + geom_bar(position = "dodge")
wor <- p + pwor + fil + geom_bar(position = "dodge")
mar <- p + pmar + fil + geom_bar(position = "dodge")

grid.arrange(gen, age, eth)
grid.arrange(inc, edu, wor, mar)

## sick plot
svychisq(~Q2 + Q13, des)
q <- svyby(~Q2, ~Q13, des, svymean, na.rm = T)
ggplot(q, aes(Q13, Q2Yes)) + geom_point() + xlab(" ") + ylab("% sick") + er +
  ggtitle(label = "% of adults sick and getting flu vaccine") 

# chisquare for getting flu vaccine and sick household member
svychisq(~Q15 + Q3, des)

```

## Q14. How much do you pay to get an influenza vaccine?

```{r}
q14 <- as.data.frame(svytable(
  ~Q14 + PPGENDER + ppagect4 + PPETHM + income + PPEDUCAT + work + marital, des, round = T))

p <- ggplot(q14, aes(Q14, weight = Freq)) + ptext
fil <- aes(fill = Q14)

p + geom_bar()
gen <- p + pgen + fil + geom_bar(position = "dodge")
age <- p + page + fil + geom_bar(position = "dodge")
eth <- p + peth + fil + geom_bar(position = "dodge") + coord_flip()
inc <- p + pinc + fil + geom_bar(position = "dodge")
edu <- p + pedu + fil + geom_bar(position = "dodge")
wor <- p + pwor + fil + geom_bar(position = "dodge")
mar <- p + pmar + fil + geom_bar(position = "dodge")

grid.arrange(gen, age, eth)
grid.arrange(inc, edu, wor, mar)

```

## Q15. Are you more likely to get a vaccine if others around you get a vaccine?

```{r}
# chisquare
svychisq(~Q15 + Q2, des)

q15 <- as.data.frame(svytable(
  ~Q15 + PPGENDER + ppagect4 + PPETHM + income + PPEDUCAT + work + marital, des, round = T))

p <- ggplot(q15, aes(Q15, weight = Freq)) + ptext
fil <- aes(fill = Q15)

p + geom_bar()
gen <- p + pgen + fil + geom_bar(position = "dodge")
age <- p + page + fil + geom_bar(position = "dodge")
eth <- p + peth + fil + geom_bar(position = "dodge") + coord_flip()
inc <- p + pinc + fil + geom_bar(position = "dodge")
edu <- p + pedu + fil + geom_bar(position = "dodge")
wor <- p + pwor + fil + geom_bar(position = "dodge")
mar <- p + pmar + fil + geom_bar(position = "dodge")

grid.arrange(gen, age, eth)
grid.arrange(inc, edu, wor, mar)

```

## Q16. Are you more likely to get a vaccine if others around you do not get a vaccine?

```{r}
# chisquare
svychisq(~Q16 + Q2, des)

q16 <- as.data.frame(svytable(
  ~Q16 + PPGENDER + ppagect4 + PPETHM + income + PPEDUCAT + work + marital, des, round = T))

p <- ggplot(q16, aes(Q16, weight = Freq)) + ptext
fil <- aes(fill = Q16)

p + geom_bar()
gen <- p + pgen + fil + geom_bar(position = "dodge")
age <- p + page + fil + geom_bar(position = "dodge")
eth <- p + peth + fil + geom_bar(position = "dodge") + coord_flip()
inc <- p + pinc + fil + geom_bar(position = "dodge")
edu <- p + pedu + fil + geom_bar(position = "dodge")
wor <- p + pwor + fil + geom_bar(position = "dodge")
mar <- p + pmar + fil + geom_bar(position = "dodge")

grid.arrange(gen, age, eth)
grid.arrange(inc, edu, wor, mar)
```

## Q17. Do you get a vaccine to protect yourself, protect others, or protect yourself and others?

```{r}
q17 <- as.data.frame(svytable(
  ~Q17 + PPGENDER + ppagect4 + PPETHM + income + PPEDUCAT + work + marital, des, round = T))

p <- ggplot(q17, aes(Q17, weight = Freq)) + ptext
fil <- aes(fill = Q17)

p + geom_bar()
gen <- p + pgen + fil + geom_bar(position = "dodge")
age <- p + page + fil + geom_bar(position = "dodge")
eth <- p + peth + fil + geom_bar(position = "dodge") + coord_flip()
inc <- p + pinc + fil + geom_bar(position = "dodge")
edu <- p + pedu + fil + geom_bar(position = "dodge")
wor <- p + pwor + fil + geom_bar(position = "dodge")
mar <- p + pmar + fil + geom_bar(position = "dodge")

grid.arrange(gen, age, eth)
grid.arrange(inc, edu, wor, mar)
```

## Q18. What are the reasons you would not get an influenza vaccine?
```{r}

```

## Q19. Do you have health insurance?

```{r}
# chisquare
svychisq(~Q19 + Q2, des)

q19 <- as.data.frame(svytable(
  ~Q19 + PPGENDER + ppagect4 + PPETHM + income + PPEDUCAT + work + marital, des, round = T))

p <- ggplot(q19, aes(Q19, weight = Freq)) + ptext
fil <- aes(fill = Q19)

p + geom_bar()
gen <- p + pgen + fil + geom_bar(position = "dodge")
age <- p + page + fil + geom_bar(position = "dodge")
eth <- p + peth + fil + geom_bar(position = "dodge") + coord_flip()
inc <- p + pinc + fil + geom_bar(position = "dodge")
edu <- p + pedu + fil + geom_bar(position = "dodge")
wor <- p + pwor + fil + geom_bar(position = "dodge")
mar <- p + pmar + fil + geom_bar(position = "dodge")

grid.arrange(gen, age, eth)
grid.arrange(inc, edu, wor, mar)

## sick plot
q <- svyby(~Q2, ~Q19, des, svymean, na.rm = T)
ggplot(q, aes(Q19, Q2Yes)) + geom_point() + xlab(" ") + ylab("% sick") + er +
  ggtitle(label = "% of adults sick and having health insurance ") 

```

## Q20. How effective do you think the influenza vaccine is in protecting people from becoming sick with influenza?

```{r}

q20 <- as.data.frame(svytable(
  ~Q20 + PPGENDER + ppagect4 + PPETHM + income + PPEDUCAT + work + marital, des, round = T))

p <- ggplot(q20, aes(Q20, weight = Freq)) + ptext
fil <- aes(fill = Q20)

p + geom_bar()
gen <- p + pgen + fil + geom_bar(position = "dodge")
age <- p + page + fil + geom_bar(position = "dodge")
eth <- p + peth + fil + geom_bar(position = "dodge") + coord_flip()
inc <- p + pinc + fil + geom_bar(position = "dodge")
edu <- p + pedu + fil + geom_bar(position = "dodge")
wor <- p + pwor + fil + geom_bar(position = "dodge")
mar <- p + pmar + fil + geom_bar(position = "dodge")

grid.arrange(gen, age, eth)
grid.arrange(inc, edu, wor, mar)

## sick plot
svychisq(~Q2 + Q20, des)
q <- svyby(~Q2, ~Q20, des, svymean, na.rm = T)
ggplot(q, aes(Q20, Q2Yes)) + geom_point() + xlab(" ") + ylab("% sick") + ptext + er +
  ggtitle(label = "% of adults sick vs. perception of flu vaccine efficacy") 

```

