---
title: "Analysis summary part 2"
output: 
  html_document:
    fig_caption: yes
    fig_height: 4
    fig_width: 6
    theme: paper
    keep_md: yes
    toc: yes
    toc_depth: 2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T, cache = T, cache.comments = T, warning = F, message = F, tidy = T, size = "small")
rm(list = ls(all.names = TRUE))
library(rmarkdown); library(knitr)
library(tidyr); library(dplyr); library(ggplot2)
library(survey); library(gridExtra)
```

```{r load-data, include=F}
## Load data variables.
load("~/git/flu-survey/data/cleaning2.RData")
load("~/git/flu-survey/data/recoding.RData")  # load "datar"
df <- datar  # contains recoded variables
```

```{r regroup-data, include=FALSE}
## income
income.map <- c(rep("under $10k", 3),
                rep("$10k to $25k", 4),
                rep("$25k to $50k", 4),
                rep("$50k to $75k", 2),
                rep("$75k to $100k", 2),
                rep("$100k to $150k", 2),
                rep("over $150k", 2))
df$income <- code(datar$PPINCIMP, income.map, "under $10k")
income.lab <- c("under $10k", "$10k to $25k", "$25k to $50k", "$50k to $75k", "$75k to $100k", "$100k to $150k", "over $150k")
df$income <- factor(df$income, levels = income.lab)

## marital staus
marital.map <- c("single", "partnered", "partnered", "single", "single", "single")
df$marital <- code(dataf$PPMARIT, marital.map, "single")

## work status
work.map <- c(rep("unemployed", 5),
              rep("employed", 2))
df$work <- code(dataf$PPWORK, work.map, "unemployed")
```

```{r survey-design}
## Create survey object.
options(digits = 4)
options(survey.lonely.psu = "adjust")

# subset data?
des <- svydesign(ids = ~1, weights = ~weight, data = df[is.na(df$weight)==F, ])
```

```{r ggplot, include=FALSE}
#### create ggplot templates ####

ptext <- theme(axis.text = element_text(size = rel(0.9)), axis.text.x = element_text(angle = 45, hjust = 1))
pgen <- aes(PPGENDER)
page <- aes(ppagect4)
peth <- aes(PPETHM)
pinc <- aes(income)
pedu <- aes(PPEDUCAT)
pwor <- aes(work)
pmar <- aes(marital)
er <- geom_errorbar(aes(ymin = Q2Yes - se.Q2Yes, ymax = Q2Yes + se.Q2Yes), width = .25)
```


## Q11. How do you rate your risk of getting influenza if you visited each of the following locations?
```{r}
# subset question data
q11df <- df %>%
  select(CaseID, PPGENDER, ppagect4, PPETHM, income, PPEDUCAT, work, marital, ppreg9, PPMSACAT, Q2, Q11_1:Q11_11, weight) %>%
  gather(Q11_q, Q11_r, Q11_1:Q11_11, na.rm = T) %>%
  group_by(Q11_q, Q11_r)

# new survey design
des11 <- svydesign(ids = ~1, weights = ~weight, data = q11df[is.na(q11df$weight)==F, ])

# weighted data frame
q11 <- data.frame(svytable(~Q11_q + Q11_r + PPGENDER + ppagect4 + PPETHM + income + PPEDUCAT + work + ppreg9 + PPMSACAT, des11, round = T))


# plot
p <- ggplot(q11, aes(Q11_r, weight = Freq)) + ptext
fil <- aes(fill = Q11_r)

p + fil + geom_bar() + facet_wrap(~Q11_q)

# gender
p + aes(fill = PPGENDER) + geom_bar(position = "dodge") + facet_wrap(~Q11_q)

# age
p + page + fil + geom_bar(position = "dodge") + facet_wrap(~Q11_q)
p + fil + geom_bar(position = "stack") + facet_wrap(~ppagect4 + ~Q11_q)

# race
p + peth + fil + geom_bar(position = "stack")
p + aes(fill = PPETHM) + geom_bar(position = "fill")

# income
p + pinc + fil + geom_bar(position = "stack")
p + aes(fill = income) + geom_bar(position = "dodge")
# metro location
p + aes(PPMSACAT) + fil + geom_bar(position = "fill")
p + aes(fill = PPMSACAT) + geom_bar(position = "stack")
# region
p + fil + geom_bar(position = "dodge") + facet_wrap(~ ppreg9)
```

## Q12. Which of the following actions do you take to avoid getting sick?
```{r}

```

## Q13. Do you get the flu vaccine?

```{r q13-plot}
q13 <- as.data.frame(svytable(
  ~Q13 + PPGENDER + ppagect4 + PPETHM + income + PPEDUCAT + work + marital, des, round = T))

p <- ggplot(q13, aes(Q13, weight = Freq)) + ptext
fil <- aes(fill = Q13)

p + geom_bar()
gen <- p + pgen + fil + geom_bar(position = "dodge")
age <- p + page + fil + geom_bar(position = "dodge")
eth <- p + peth + fil + geom_bar(position = "dodge") + coord_flip()
inc <- p + pinc + fil + geom_bar(position = "dodge")
edu <- p + pedu + fil + geom_bar(position = "dodge")
wor <- p + pwor + fil + geom_bar(position = "dodge")
mar <- p + pmar + fil + geom_bar(position = "dodge")

grid.arrange(gen, age, eth)
grid.arrange(inc, edu, wor, mar)

## sick plot
svychisq(~Q2 + Q13, des)
q <- svyby(~Q2, ~Q13, des, svymean, na.rm = T)
ggplot(q, aes(Q13, Q2Yes)) + geom_point() + xlab(" ") + ylab("% sick") + er +
  ggtitle(label = "% of adults sick and getting flu vaccine") 

# chisquare for getting flu vaccine and sick household member
svychisq(~Q15 + Q3, des)

```

## Q14. How much do you pay to get an influenza vaccine?

```{r}
q14 <- as.data.frame(svytable(
  ~Q14 + PPGENDER + ppagect4 + PPETHM + income + PPEDUCAT + work + marital, des, round = T))

p <- ggplot(q14, aes(Q14, weight = Freq)) + ptext
fil <- aes(fill = Q14)

p + geom_bar()
gen <- p + pgen + fil + geom_bar(position = "dodge")
age <- p + page + fil + geom_bar(position = "dodge")
eth <- p + peth + fil + geom_bar(position = "dodge") + coord_flip()
inc <- p + pinc + fil + geom_bar(position = "dodge")
edu <- p + pedu + fil + geom_bar(position = "dodge")
wor <- p + pwor + fil + geom_bar(position = "dodge")
mar <- p + pmar + fil + geom_bar(position = "dodge")

grid.arrange(gen, age, eth)
grid.arrange(inc, edu, wor, mar)

```

## Q15. Are you more likely to get a vaccine if others around you get a vaccine?

```{r}
# chisquare
svychisq(~Q15 + Q2, des)

q15 <- as.data.frame(svytable(
  ~Q15 + PPGENDER + ppagect4 + PPETHM + income + PPEDUCAT + work + marital, des, round = T))

p <- ggplot(q15, aes(Q15, weight = Freq)) + ptext
fil <- aes(fill = Q15)

p + geom_bar()
gen <- p + pgen + fil + geom_bar(position = "dodge")
age <- p + page + fil + geom_bar(position = "dodge")
eth <- p + peth + fil + geom_bar(position = "dodge") + coord_flip()
inc <- p + pinc + fil + geom_bar(position = "dodge")
edu <- p + pedu + fil + geom_bar(position = "dodge")
wor <- p + pwor + fil + geom_bar(position = "dodge")
mar <- p + pmar + fil + geom_bar(position = "dodge")

grid.arrange(gen, age, eth)
grid.arrange(inc, edu, wor, mar)

```

## Q16. Are you more likely to get a vaccine if others around you do not get a vaccine?

```{r}
# chisquare
svychisq(~Q16 + Q2, des)

q16 <- as.data.frame(svytable(
  ~Q16 + PPGENDER + ppagect4 + PPETHM + income + PPEDUCAT + work + marital, des, round = T))

p <- ggplot(q16, aes(Q16, weight = Freq)) + ptext
fil <- aes(fill = Q16)

p + geom_bar()
gen <- p + pgen + fil + geom_bar(position = "dodge")
age <- p + page + fil + geom_bar(position = "dodge")
eth <- p + peth + fil + geom_bar(position = "dodge") + coord_flip()
inc <- p + pinc + fil + geom_bar(position = "dodge")
edu <- p + pedu + fil + geom_bar(position = "dodge")
wor <- p + pwor + fil + geom_bar(position = "dodge")
mar <- p + pmar + fil + geom_bar(position = "dodge")

grid.arrange(gen, age, eth)
grid.arrange(inc, edu, wor, mar)
```

## Q17. Do you get a vaccine to protect yourself, protect others, or protect yourself and others?

```{r}
q17 <- as.data.frame(svytable(
  ~Q17 + PPGENDER + ppagect4 + PPETHM + income + PPEDUCAT + work + marital, des, round = T))

p <- ggplot(q17, aes(Q17, weight = Freq)) + ptext
fil <- aes(fill = Q17)

p + geom_bar()
gen <- p + pgen + fil + geom_bar(position = "dodge")
age <- p + page + fil + geom_bar(position = "dodge")
eth <- p + peth + fil + geom_bar(position = "dodge") + coord_flip()
inc <- p + pinc + fil + geom_bar(position = "dodge")
edu <- p + pedu + fil + geom_bar(position = "dodge")
wor <- p + pwor + fil + geom_bar(position = "dodge")
mar <- p + pmar + fil + geom_bar(position = "dodge")

grid.arrange(gen, age, eth)
grid.arrange(inc, edu, wor, mar)
```

## Q18. What are the reasons you would not get an influenza vaccine?
```{r}

```

## Q19. Do you have health insurance?

```{r}
# chisquare
svychisq(~Q19 + Q2, des)

q19 <- as.data.frame(svytable(
  ~Q19 + PPGENDER + ppagect4 + PPETHM + income + PPEDUCAT + work + marital, des, round = T))

p <- ggplot(q19, aes(Q19, weight = Freq)) + ptext
fil <- aes(fill = Q19)

p + geom_bar()
gen <- p + pgen + fil + geom_bar(position = "dodge")
age <- p + page + fil + geom_bar(position = "dodge")
eth <- p + peth + fil + geom_bar(position = "dodge") + coord_flip()
inc <- p + pinc + fil + geom_bar(position = "dodge")
edu <- p + pedu + fil + geom_bar(position = "dodge")
wor <- p + pwor + fil + geom_bar(position = "dodge")
mar <- p + pmar + fil + geom_bar(position = "dodge")

grid.arrange(gen, age, eth)
grid.arrange(inc, edu, wor, mar)

## sick plot
q <- svyby(~Q2, ~Q19, des, svymean, na.rm = T)
ggplot(q, aes(Q19, Q2Yes)) + geom_point() + xlab(" ") + ylab("% sick") + er +
  ggtitle(label = "% of adults sick and having health insurance ") 

```

## Q20. How effective do you think the influenza vaccine is in protecting people from becoming sick with influenza?

```{r}

q20 <- as.data.frame(svytable(
  ~Q20 + PPGENDER + ppagect4 + PPETHM + income + PPEDUCAT + work + marital, des, round = T))

p <- ggplot(q20, aes(Q20, weight = Freq)) + ptext
fil <- aes(fill = Q20)

p + geom_bar()
gen <- p + pgen + fil + geom_bar(position = "dodge")
age <- p + page + fil + geom_bar(position = "dodge")
eth <- p + peth + fil + geom_bar(position = "dodge") + coord_flip()
inc <- p + pinc + fil + geom_bar(position = "dodge")
edu <- p + pedu + fil + geom_bar(position = "dodge")
wor <- p + pwor + fil + geom_bar(position = "dodge")
mar <- p + pmar + fil + geom_bar(position = "dodge")

grid.arrange(gen, age, eth)
grid.arrange(inc, edu, wor, mar)

## sick plot
svychisq(~Q2 + Q20, des)
q <- svyby(~Q2, ~Q20, des, svymean, na.rm = T)
ggplot(q, aes(Q20, Q2Yes)) + geom_point() + xlab(" ") + ylab("% sick") + ptext + er +
  ggtitle(label = "% of adults sick vs. perception of flu vaccine efficacy") 

```

