---
title: "Comparing weighted and unweighted survey data"
output: 
  html_document:
    keep_md: yes
    toc: yes
    toc_depth: 2
---

# Comparing weighted and unweighted survey data

```{r setup, include=FALSE}
knitr::opts_chunk$set(cache = T, echo = T, warning = F, message = F, tidy = F, size = "small")
rm(list = ls(all.names = TRUE))
library(rmarkdown); library(dplyr); library(ggplot2); library(survey);
library(gridExtra)
```

```{r}
## Load data variables.

load("~/git/flu-survey/data/cleaning2.RData")
load("~/git/flu-survey/data/recoding.RData")  # load "datar"
df <- datar  # contains recoded variables
```

```{r des}
## Create survey object.

options(digits = 4)
options(survey.lonely.psu = "adjust")
des <- svydesign(ids = ~1, weights = ~weight, data = df[is.na(df$weight) == F, ])
```

### Example of Q1 by gender.

```{r example}
## Example tables of Q1 by gender.

as.data.frame(svytable(~Q1 + PPGENDER, design = des, round = T))  # weighted counts
svyby(~Q1, ~Q1+PPGENDER, des, unwtd.count)  # unweighted counts
svyby(~Q1, ~PPGENDER, design = des, FUN = svymean, na.rm = T)  # weighted %
plot(svytable(~Q1 + PPGENDER, des))  # default survey plot

## generic ggplot
# ggplot(data.frame.here, aes(Q1, Freq, fill = PPGENDER) + geom_bar(stat = 'identity', position = position_dodge())
```

## Q1.

### By demographic variables:
- gender, ethnicity, age, education, income, employment, marital status, metro location, region, house type, head of household, rent status, state, internet availability

```{r q1}
# save freq table as data.frame
q1 <- as.data.frame(svytable(
  ~Q1 + PPGENDER + PPETHM + ppagect4, design = des, round = T))

# make ggplot object
g1 <- ggplot(q1)
g1 + aes(Q1, Freq, fill = PPGENDER) + 
  geom_bar(stat = 'identity', position = position_dodge())
g1 + aes(Q1, Freq, fill = PPETHM) + 
  geom_bar(stat = 'identity', position = position_dodge())
g1 + aes(Q1, Freq, fill = ppagect4) + 
  geom_bar(stat = 'identity', position = position_stack())

```

### Examine the % of US adults sick with ILI last year by sex, ethnicity, and age. Do a survey-corrected chi-square test for independence.

```{r}
## % of US adults sick last year with ILI by sex
sex <- svyby(formula = ~Q2, by = ~PPGENDER, design = des, FUN = svymean, na.rm = T)
svychisq(~Q2 + PPGENDER, design = des)

qplot(x = sex$PPGENDER, y = sex$Q2Yes, data = sex, xlab = "sex", ylab = "% sick") + geom_errorbar(aes(x = PPGENDER, ymin = Q2Yes - se.Q2Yes, ymax = Q2Yes + se.Q2Yes), width = .25) + ggtitle(label = "% of adults sick last year with ILI by sex")

## % of US adults sick last year with ILI by ethnicity
eth <- svyby(formula = ~Q2, by = ~PPETHM, design = des, FUN = svymean, na.rm = T)
svychisq(~Q2 + PPETHM, design = des)

qplot(x = eth$PPETHM, y = eth$Q2Yes, data = eth, xlab = "ethnicity", ylab = "% sick") + geom_errorbar(aes(x = PPETHM, ymin = Q2Yes - se.Q2Yes, ymax = Q2Yes + se.Q2Yes), width = .25) + ggtitle(label = "% of adults sick last year with ILI by ethnicity")

## % of US adults sick last year with ILI by age
age <- svyby(formula = ~Q2, by = ~ppagecat, design = des, FUN = svymean, na.rm = T)
svychisq(~Q2 + ppagecat, design = des)

qplot(x = age$ppagecat, y = age$Q2Yes, data = age, xlab = "age", ylab = "% sick") + geom_errorbar(aes(x = ppagecat, ymin = Q2Yes - se.Q2Yes, ymax = Q2Yes + se.Q2Yes), width = .25) + ggtitle(label = "% of adults sick last year with ILI by age")
```

### Simple weighted plots.

```{r}
## weighted bivariate plots with svytable
qtest <- as.data.frame(svytable(
  ~Q1 + PPGENDER + PPETHM + ppagect4, design = des, round = T))

p <- ggplot(qtest, aes(weight = Freq))

#svytable(~Q1 + PPGENDER, des, round = T)
(a <- p + aes(PPGENDER, fill = Q1) + geom_bar(width = 0.7, position = "fill"))

#svytable(~Q1 + PPETHM, des, round = T)
(b <- p + aes(PPETHM, fill = Q1) + geom_bar(width = 0.7, position = "fill") +
  geom_point(aes(y = -0.05), size = 0.75, alpha = 0.3, position = position_jitter(h = 0.01)))

#svytable(~Q1 + ppagect4, des, round = T)
(c <- p + aes(ppagect4, fill = Q1) + geom_bar(position = "fill") +
  geom_point(aes(y = -0.05), size = 0.75, alpha = 0.3, position = position_jitter(h = 0.01)))

grid.arrange(a, b, c)
```

### Compare weighted plots to unweighted plots.

```{r}
## unweighted plots
q <- ggplot(df[!is.na(df$Q1), ])

with(df, table(PPGENDER, Q1))
a <- q + geom_bar(aes(PPGENDER, fill = Q1), position = "dodge")

with(df, table(PPETHM, Q1))
b <- q + geom_bar(aes(Q1, fill = PPETHM), position = "dodge")

with(df, table(ppagect4, Q1))
c <- q + geom_bar(aes(Q1, fill = ppagect4), position = "dodge")

grid.arrange(a, b, c)
```


```{r, eval=FALSE, include=FALSE}
## testing ##

# boxplot for age
boxplot(PPAGE ~ Q2, data = df, ylab = "age", xlab = "Q2. Have you had an illness with ILI symptoms since August 2015?", main = "Boxplot of age of sick adults")

# multiple univariate plots
temp <- c("Q1", "Q2", "Q3")
par(mfrow = c(1, 3))

for (i in temp)
  barplot(table(df[, i]), main = i, ylab = "n")
```



